\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
		\item Find $\abs{\overrightarrow{a}\times\overrightarrow{b}},\text{ if }\overrightarrow{a}=\hat{i}-7\hat{j}+7\hat{k}\text{ and } \overrightarrow{b}=3\hat{i}-2\hat{j}+2\hat{k}$.
	\\
		\solution
		\input{chapters/12/10/4/1/cross.tex}
\item Find $\lambda$ and $\mu$ if $(2\hat{i}+6\hat{j}+27\hat{k})\times(\hat{i}+\lambda \hat{j} + \mu \hat{k})=\overrightarrow{0}$.
	\\
		\solution
		\input{chapters/12/10/4/5/cross.tex}
\item Find the area of the triangle with vertices $A(1, 1, 2), B(2, 3, 5)$ and $C(1, 5, 5)$.
	\\
		\solution
		\input{chapters/12/10/4/9/cross.tex}
\item Find the area of the parallelogram whose adjacent sides are determined by the vectors $\overrightarrow{a}=\hat{i}-\hat{j}+3\hat{k}$ and $\overrightarrow{b}=2\hat{i}-7\hat{j}+\hat{k}$.
	\\
		\solution
		\input{chapters/12/10/4/10/cross.tex}
\item Find the area of a rhombus if its vertices are $A(3,0), B(4,5), C(-1,4)$  and  $D(-2,-1)$ taken in order. 
	\\
		\solution
	\input{chapters/10/7/2/10/cross.tex}
\item Let the vectors $\overrightarrow{a}$ and $\overrightarrow{b}$ be such that $|\overrightarrow{a}| = 3$ and $|\overrightarrow{b}| = \dfrac{\sqrt{2}}{3}$, then $\overrightarrow{a} \times \overrightarrow{b}$ is a unit vector, if the angle between $\overrightarrow{a}$ and $\overrightarrow{b}$ is
\begin{enumerate}
\item $\frac{\pi}{6}$
\item $\frac{\pi}{4}$
\item $\frac{\pi}{3}$
\item $\frac{\pi}{2}$
\end{enumerate}
		\solution
		\input{chapters/12/10/4/11/cross.tex}
\item Area of a rectangle having vertices A, B, C and D with position vectors $ -\hat{i}+ \frac{1}{2} \hat{j}+4\hat{k}, \hat{i}+ \frac{1}{2} \hat{j}+4\hat{k}, \hat{i}-\frac{1}{2} \hat{j}+4\hat{k}$ and $-\hat{i}- \frac{1}{2} \hat{j}+4\hat{k}$, respectively is
\begin{enumerate}
\item $\frac{1}{2}$
\item 1
\item 2
\item 4
\end{enumerate}
		\solution
		\input{chapters/12/10/4/12/cross.tex}
\item Find the area of the triangle whose vertices are 
\begin{enumerate}
\item $(2, 3), (–1, 0), (2, – 4)$
\item $(–5, –1), (3, –5), (5, 2)$ 
\end{enumerate}
		\label{10/7/3/1}
\solution
		\input{chapters/10/7/3/1/area.tex}
\item Find the area of the triangle formed by joining the mid-points of the sides of the triangle whose vertices are $A(0, –1), B(2, 1)$  and  $C(0, 3)$. Find the ratio of this area to the area of the given triangle.
	\\
\solution
		\input{chapters/10/7/3/3/cross.tex}

\item Find the area of the quadrilateral whose vertices, taken in order, are $A(– 4, – 2), B(– 3, – 5), C(3, – 2)$  and $ D(2, 3)$.
	\\
\solution
		\input{chapters/10/7/3/4/cross.tex}

\item Verify that a median of a triangle divides it into two triangles of equal areas for $\triangle ABC$ whose vertices are $\vec{A}(4, -6), \vec{B}(3, 2), \text{ and } \vec{C}(5, 2)$. 
		\label{10/7/3/5}
		\\
\solution
		\input{chapters/10/7/3/5/area.tex}
\item The two adjacent sides of a parallelogram are 
$\vec{a}= 2\hat{i}-4\hat{j}+5\hat{k}$  and  $\vec{b} =\hat{i}-2\hat{j}-3\hat{k}$.
Find the unit vector parallel to its diagonal. Also, find its area.\\
	\solution
		\input{chapters/12/10/5/10/cross.tex}
\item The vertices of a $\triangle ABC$ are $\vec{A}(4,6), \vec{B}(1,5)$ and  $\vec{C}(7,2)$. A line is drawn to intersect sides $AB$ and $AC$ at $\vec{D}$ and $\vec{E}$ respectively, such that $\frac{AD}{AB} = \frac{AE}{AC} = \frac{1}{4}$. Calculate the area of $\triangle ADE$ and compare it with the area of the $\triangle ABC$.
\\
\solution
	\input{chapters/10/7/4/6/section.tex}
    \item Draw a quadrilateral in the Cartesian plane, whose vertices are 
    \begin{align}
        \vec{A} = \myvec{-4\\5},\, \vec{B} = \myvec{0\\7},\, 
        \vec{C} = \myvec{5\\-5},\, \vec{D} = \myvec{-4\\-2}.
    \end{align}
    Also, find its area.
\label{chapters/11/10/1/1}
   \\ 
    \solution 
\input{chapters/11/10/1/1/cross.tex}
\item Find the area of region bounded by the triangle whose
	vertices are $(1, 0), (2, 2) \text{ and } (3, 1)$. 
\item Find the area of region bounded by the triangle whose vertices
	are $(– 1, 0), (1, 3) \text{ and } (3, 2)$. 
\item Find the area of the $\triangle ABC$, coordinates of whose vertices are $\vec{A}(2, 0), \vec{B}(4, 5), \text{ and } \vec{C}(6, 3)$.
\item Show that $$(\overrightarrow{a}-\overrightarrow{b})\times (\overrightarrow{a}+\overrightarrow{b})=2(\overrightarrow{a}\times \overrightarrow{b})$$
	\\
		\solution
		\input{chapters/12/10/4/4/cross.tex}
\item If either $\overrightarrow{a} = \overrightarrow{0}$ or $\overrightarrow{b} = \overrightarrow{0}$, then $\overrightarrow{a} \times \overrightarrow{b} = \overrightarrow{0}$. Is the converse true? Justify your answer with an example.
	\\
		\solution
		\input{chapters/12/10/4/8/cross.tex}
\item Given that $\overrightarrow{a} \cdot \overrightarrow{b} = 0$ and $\overrightarrow{a} \times \overrightarrow{b} = \overrightarrow{0}$. What can you conclude about the vectors $\overrightarrow{a} \text{ and }\overrightarrow{b}$?
\item The area of a triangle with vertices $\vec{A}(3, 0), \vec{B}(7, 0)$ and  $\vec{C}(8, 4)$ is
\begin{enumerate}
\item 14
\item 28
\item 8
\item 6
\end{enumerate}
\item The area of a triangle with vertices $(a,b+c), (b,c+a)\text{ and }(c,a+b)$ is
\begin{enumerate}
\item $(a+b+c)^2$
\item 0
\item a+b+c
\item abc 
\end{enumerate}
\item Find the area of the triangle whose vertices are $(-8,4),(-6,6)$and $(-3,9)$.
\item If $\vec{D}\brak{\frac{-1}{2},\frac{5}{2}},\vec{E}(7,3)$ and $\vec{F}\brak{\frac{7}{2},\frac{7}{2}}$ are the midpoints of sides of $\triangle ABC$, find the area of the $\triangle ABC$.
\item If $\vec{a}+\vec{b}+\vec{c}$=0, show that $\vec{a}\times\vec{b}=\vec{b}\times\vec{c}=\vec{c}\times\vec{a}$. Interpret the result geometrically.
\item Find the sine of the angle between the vectors $\vec{a}=3\hat{i}+\hat{j}+2\hat{k}$ $\text{ and }$ $\vec{b}=2\hat{i}-2\hat{j}+4\hat{k}$.
\item Using vectors, find the area of $\triangle{ABC}$ with vertices A(1,2,3), B(2,-1,4) and C(4,5,-1).
\item Using vectors, prove that the parallelograms on the same base and between the same parallels are equal in area.
\item If $\vec{a}, \vec{b}, \vec{c}$, determine the vertices of a triangle, show that $\frac{1}{2}$ $\left[\vec{b} \times\vec{c}+\vec{c} \times\vec{a}+\vec{a}\times\vec{b} \right]$ gives the vector area of the triangle. Hence deduce the condition that the three points $\vec{a},\vec{b},\vec{c},$ are collinear. Also find the unit vector normal to the plane of the triangle.
\item Find the area of the parallelogram whose diagonals are $2\hat{i}-\hat{j}+\hat{k}$ and $\hat{i}+3\hat{j}-\hat{k}$.

\item The vector from origin to the points A and B are $\vec{a}$ = $2\hat{i}-3\hat{j}+2\hat{k}$ and  $\vec{b}$ = $2\hat{i}+3\hat{j}+\hat{k}$, respectively, then the area of $\triangle {OAB}$ is
	\begin{enumerate}
\item 340 
\item $\sqrt{25}$
\item $\sqrt{229}$
\item $\frac{1}{2}\sqrt{229}$
\end{enumerate}
\item For any vector $\vec{a}$, the value of $(\vec{a}\times\hat{i})^2+(\vec{a}\times\hat{j})^2 + (\vec{a}\times\hat{k})^2$ is equal to 
	\begin{enumerate}
\item a 
\item 3a
\item 4a
\item 2a
\end{enumerate}


\item If $\abs{\vec{a}}=10, \abs{\vec{b}}=2$ and $\vec{a}, \vec{b}$=12, then value of $\abs{\vec{a}\times\vec{b}}$ is
	\begin{enumerate}
\item 5 
\item 10 
\item 14 
\item 16
\end{enumerate}
\item If $\vec{a} = \hat{i}+\hat{j}+\hat{k}$ and $\vec{b} = \hat{j}-\hat{k}$, find a vector $\vec{c}$ such that $\vec{a}\times\vec{c} = \vec{b}$ and $\vec{a}\cdot \vec{c}$ = 3.
%
\item The area of the quadrilateral ABCD, where A$(0,4,1)$, B$(2,3,-1)$, C$(4,5,0)$ and D$(2,6,2)$, is equal to 
\begin{enumerate}
	\item 9 sq. units
	\item 18 sq. units 
	\item 27 sq. units 
	\item 81 sq. units
\end{enumerate}
\item Find the area of region bounded by the triangle whose vertices are (-1, 1), (0, 5) and (3, 2).
\end{enumerate}

