\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item Find the slope of a line, which passes through the origin and the mid point of the line segment joining the points $\vec{P}$(0,-4) and $\vec{B}$(8,0).
\label{chapters/11/10/1/5}
	\\
	\solution
\input{chapters/11/10/1/5/matrix.tex}
\item A line passes through $A(x_1,y_1)$ and $B(h,k)$. If slope of the line is m, show that $(k-y_1)=m(h-x_1)$.
\label{chapters/11/10/1/12}
\\
\solution 
\input{chapters/11/10/1/12/matrix.tex}
\item
Show that the line through the points \brak{4,7,8},\brak{2,3,4} is parallel to the line through the points \brak{-1,-2,1},\brak{1,2,5}.
	\label{12.11.2.3}
\\
\solution
	\input {chapters/12/11/2/3/vec2.tex}
\item For given vectors, $\vec{a}=2\hat{i}-\hat{j}+2\hat{k}$ and $\vec{b}=-\hat{i}+\hat{j}-\hat{k}$ , find the unit vector in the
direction of the vector $\vec{a}+\vec{b}$.
        \label{prob:12/10/2/9}
\\
    \solution 
		\input{chapters/12/10/2/9/norm.tex}
\item Find a vector of magnitude 5 units, and parallel to the resultant of the vectors $\vec{a}=2\hat{i}+3\hat{j}-\hat{k}$ and $\vec{b}=\hat{i}-2\hat{j}+\hat{k}$.\\
\item If $\vec{a}=\hat{i}+\hat{j}+\hat{k}, \vec{b}=2\hat{i}-\hat{j}+3\hat{k}$ and $\vec{c}=\hat{i}-2\hat{j}+\hat{k}$, find a unit vector parallel to the vector $2\vec{a}-\vec{b}+3\vec{c}$.\\
	\solution
		\input{chapters/12/10/5/7/norm.tex}
\item Find a vector in the direction of vector $5\hat{i}-\hat{j}+2\hat{k}$ which has magnitude 8 units.
        \label{prob:12/10/2/10const}
   \\ 
    \solution 
		\input{chapters/12/10/2/10/norm.tex}
\item Find the unit vector in the direction of the vector $\vec{a}=\hat{i}+\hat{j}+2\hat{k}$.
\item Find the unit vector in the direction of vector $\overrightarrow{PQ}$ , where $\vec{P}$ and $\vec{Q}$ are the points
(1, 2, 3) and (4, 5, 6), respectively.
	\item 
Find a vector of magnitude 5 units, and parallel to the resultant of the vectors $\vec{a} = 2\hat{i}+3\hat{j}-\hat{k}$ and $\vec{b} = \hat{i}-2\hat{j}+\hat{k}$.
\\
\solution
		\input{chapters/12/10/5/6/asgnt2.tex}
	\item If a line makes angles $90\degree,135\degree,45\degree$ with x,y and z-axis respectivly. Find its direction cosines.
		\\
		\solution
		\input{chapters/12/11/1/1/vec.tex}
\item Find the direction cosines of the vector joining the points $\vec{A}$ (1, 2, –3) and
$\vec{B}$(–1, –2, 1), directed from $\vec{A}$ to $\vec{B}$.
	\\
    \solution 
		\input{chapters/12/10/2/13/norm.tex}
\item Show that the vector $\hat{i}+\hat{j}+\hat{k}$ is equally inclined to the axes OX, OY and OZ.
	\\
\solution
		\input{chapters/12/10/2/14/inner.tex}
\item If a line has the direction ratios –18, 12, –4, then what are its direction cosines?
		\\
		\solution
		\input{chapters/12/11/1/3/norm.tex}
	\item Find the direction cosines of the sides of a triangle whose vertices are $\myvec{3\\ 5\\-4 }$, $\myvec{ -1\\1 \\2 }$ and $\myvec{-5 \\-5 \\-2 }$.
		\\
		\solution
		\input{chapters/12/11/1/5/inner.tex}
\item Find the direction cosines of the vector $\hat{i}+2\hat{j}+3\hat{k}$.
	\\
    \solution 
		\input{chapters/12/10/2/12/inner.tex}
    \item Find the direction cosines of a line which makes equal angles with the coordinate
    axes.
		\\
		\solution
		\input{chapters/12/11/1/2/norm.tex}
\item Write down a unit vector in XY-plane, making an angle of 30$\degree$ with the positive direction of x-axis.\\
\item the unit vector normal to the plane $x+2y+3z-6=0$ is $\dfrac{1}{\sqrt{14}}\hat{i} + \dfrac{2}{\sqrt{14}}\hat{j} + \dfrac{3}{\sqrt{14}}\hat{k}$.
\end{enumerate}
