\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item The two opposite vertices of a square are $(–1, 2)$  and $ (3, 2)$. Find the coordinates of the other two vertices.
\\
\solution
	\input{chapters/10/7/4/4/affine.tex}
\item The base of an equilateral triangle with side $2a$ lies along the y-axis such that the mid-point of the base is at the origin. Find vertices of the triangle.
\label{chapters/11/10/1/2}
\input{chapters/11/10/1/2/matrix.tex}
\item The value of the expression $\abs{\vec{a}\times\vec{b}}$+ $({\vec{a}.\vec{b}})$ is \rule{1cm}{0.15mm}.
\item If $\abs{\vec{a}\times\vec{b}}^2$ + $\abs{\vec{a}.\vec{b}}^2$=144 $\text{and}$  $\abs{\vec{a}}$=4, then $\abs{\vec{b}}$ is equal to \rule{1cm}{0.15mm}.
\item If the directions cosines of a line are $(k,k,k)$ then
\begin{enumerate}
	\item $k>0$
	\item $0<k<1$
	\item $k=1$ 
	\item $k=\dfrac{1}{\sqrt{3}}$ or $-\dfrac{1}{\sqrt{3}}$
\end{enumerate}
\item  Find the position vector of a point A in space such that $\overrightarrow{OA}$ is inclined at $60 \degree$ to OX and at $45 \degree$ to OY and $\abs{\overrightarrow{OA}} =10$ units.
\item If $(-4,3)\text{ and }(4,3)$ are two vertices of an equilateral triangle. Find the coordinates of the third vertex, given that the origin lies in the interior of the triangle. 
\item $\vec{A} (6,1),\vec{B}(8,2) \text{ and } \vec{C}(9,4)$ are three vertices of a parallelogram ABCD. If $\vec{C}$ is the midpoint of DC find the area of $\triangle ADE$
\item If the points  $\vec{A}(1,-2), \vec{B}(2,3) , \vec{C}(a,2)\text{ and }\vec{D} (-4-3)$ form parallelogram, find the value of $a$ and height of the parallelogram taking AB as base.
\item Ayush starts walking from his house to office. Instead of going to the office directly, he goes to a bank first, from there to his daughter school and then reaches the office what is the extra distance travelled by Ayush in reaching his office? (Assume that all distanes covered are in straight lines). If the house is situated at $(2,4)$, bank at $(5,8)$, school at $(13,14)$ and office at $(13,26)$ and coordinates are in km.
\item Draw a right triangle ${ABC}$ in which $BC=12$ cm, $AB=5$ cm and $\angle{B}=90\degree$.
\item Draw a triangle ${ABC}$ in which $AB$=4 cm, $BC=6 cm\text{ and }AC=9$. 
\item Draw a triangle ${ABC}$ in which $AB$=5 cm. $BC=6 cm\text{ and }\angle {ABC}=60\degree$. 
\item Draw a parallelogram ${ABCD}$ in which $BC=5$ cm, $AB=3$ cm and $\angle{ABC}=60\degree$, divide it into triangles ${ACB}\text{ and }{ABD}$ by the diagonal $BD$. 
Construct the triangle $BD'C'$ similar to $\triangle{BDC}$ with scale factor $\frac{4}{3}$. Draw the line segment $D'A'$ parallel to $DA$ where $\vec{A}$' lies on extended side $BA$. Is $A'BC'D'$ a parallelogram? 
\item Draw a triangle ${ABC}$ in which $BC=6$ cm, $CA=5$ cm and $AB=4$ cm. 
\end{enumerate}
