\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item Determine if the points $(1,5),(2,3)$ and $(-2,-11)$ are collinear.
	\\
	\solution
Use		\eqref{prop:lin-dep-rank}.
%		\input{chapters/10/7/1/3/rank.tex}
\item Show that the points $\vec{A}(1,2,7), \vec{B}(2,6,3)$ and $\vec{C}(3,10,-1)$ are collinear.
	\\
	\solution
%		\input{chapters/12/10/3/16/rank.tex}
\item Show that the vectors $2\hat{i}-3\hat{j}+4\hat{k}$ and $-4\hat{i}+6\hat{j}-8\hat{k}$ are collinear.
   \\ 
    \solution 
%		\input{chapters/12/10/2/11/rank.tex}
\item Show that the points (2, 3, 4), (–1, –2, 1), (5, 8, 7) are collinear.
		\\
		\solution
	%	\input{chapters/12/11/1/4/rank.tex}
\item In each of the following, find the value of '$k$', for which the points are collinear.
\begin{enumerate}
\item $(7, –2), (5, 1), (3, k)$
\item $(8, 1), (k, – 4), (2, –5)$
\end{enumerate}
		\label{10/7/3/2}
\solution
	%	\input{chapters/10/7/3/2/rank.tex}
\item Find a relation between $x$ and $y$ if the points $(x, y), (1, 2)$  and  $(7, 0)$ are collinear.
\\
\solution
	%\input{chapters/10/7/4/2/rank.tex}
\item If three points $(x, -1), (2, 1)$ and $(4, 5)$ are collinear, find the value of $x$.
\label{chapters/11/10/1/8}
%\input{chapters/11/10/1/8/matrix.tex}
\item If three points $(h, 0), (a, b)$ and $(0, k)$ lie on a line, 
show that 
\begin{align}
\frac{a}{h}+\frac{b}{k}=1
\end{align}
\label{chapters/11/10/1/13}
%\input{chapters/11/10/1/13/matrix.tex}
\item Show that the points A (1, -2, -8), B (5, 0, -2) and C (11, 3, 7) are collinear, and find the ratio in which B divides AC.\\
\item lf the points $\vec{A}(1,2),\vec{0}(0,0)\text{ and }\vec{C}(a,b)$ are collinear,then
\begin{enumerate}
\item a=b
\item a=2b
\item 2a=b
\item a=-b
\end{enumerate}
\end{enumerate}
True/false
\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi,resume*]
	\item $\triangle\vec{A}\vec{B}\vec{C}$ with vertices $\vec{A}(-2,0), \vec{B}(2,0) \text{ and }\vec{C}(0,2)$ is similar to $\triangle \vec{DEF}$  with vertices $\vec {D}(-4,0),\vec{E}(4,0)  \text{ and } \vec{F}(0,4)$  
	\item Point $ (-4,2)$ lies on the line segment joining the points $ \vec{A}(-4,6) \text{ and } \vec{B}(-4,-6)$
 \item The points $(0,5),(0,-9)\text{ and }(3,6)$ are collinear
\item Points $\vec{A}(3,1), \vec{B}(12,-2) \text{ and } \vec {C}(0,2)$ cannot be the vertices of a triangle
\item Find the value of $m$ if the points $(5,1),(-2,-3) \text{ and }(8,2m)$ are collinear.
\item Find the values of k if the points $\vec{A}(k+1,2k),\vec{B}(3k,2k+3)\text{ and }\vec{C}(5k-1,5k)$ are collinear
\item Using vectors, find the value of $k$ such that the points $(k,-10,3)$, $(1,-1,3)$ $\text{ and }$ $(3,5,3)$ are collinear.
\end{enumerate}
