Find out whether the lines representing the following pairs of linear equations intersect at a point, are parallel or coincident
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item \begin{align}
	5x-4y+8=0\\ 
      	7x+6y-9=0
	\end{align}
\item \begin{align}
	9x+3y+12=0\\
	18x+6y+24=0
	\end{align}
\item \begin{align}
        6x-3y+10=0\\
	2x-y+9=0
	\end{align}
	\item \begin{align}
       		3x+2y=5; \\
      		2x-3y=7
    	       \end{align} 
	\item \begin{align}
		2x-3y=8;\\
		4x-6y=9
		\end{align}
	\item \begin{align}
		\frac{3}{2}x+\frac{5}{3}y=7;\\
		9x-10y=14
		\end{align}
\item \begin{align}
		5x-3y=11;\\
		-10x+6y=-22
	\end{align}
\item \begin{align}
         \frac{4}{3}x+2y=8;\\
	  2x+3y=12
	\end{align}
\item \begin{align}
	x+y=5;\\
	2x+y=10
	\end{align}
\item \begin{align}
	x-y=8;\\
	3x-3y=16
	\end{align}
\item \begin{align}
 	2x+y-6=0;\\
 	4x-2y+4=0
	\end{align}
\item \begin{align}
	2x-2y-2=0;\\
	4x-4y-5=0
	\end{align}
	\item \begin{align}
	x-3y-3=0\\
	3x-9y-2=0
        \end{align}
       \item \begin{align}
	2x+y=5\\
	3x+2y=8
	\end{align}
	\item \begin{align}
	3x-5y=20\\
	6x-10y=40
	\end{align}
	\item \begin{align}
	x-3y-7=0\\
	3x-3y-15=0
        \end{align}
\item \begin{align}
8x+5y=9
\\ 3x+2y=4
\end{align}
\end{enumerate}
Form the pair of linear equations in the following problems and find their solutions graphically
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi, resume*]
\item $10$ students of Class X took part in a Mathematics quiz. If the number of girls is $4$ more than the number of boys, find the number of boys and girls who took part in the quiz.
\item $5$ pencils and $7$ pens together cost $Rs. 50$ whereas $7$ pencils and $5$ pens together cost $Rs. 46$. Find the cost of one pencil and that of one pen.
\item Half the perimeter of a rectangular garden, whose length is $4m$, more than its width, is $36m$. Find the dimensions of the garden.
\item A part of monthly hostel charges is fixed and the remaining depends on the number of days one has taken food in the mess. When a student $A$ takes food for $20$ days she has to pay Rs.$1000$ as hostel charges whereas a student $B$ who takes food for $26$ days, pays Rs.$1180$ as hostel charges. Find the fixed charges and the cost of food per day.
\item A fraction becomes $\frac{1}{3}$ when $1$ is subtracted from the numerator and it becomes $\frac{1}{4}$ when $8$ is added to the denominator. Find the fraction.
\item Yash scored $40$ marks in a test, getting $3$ marks for each right answer and losing $1$ mark for each wrong answer. Had $4$ marks been awarded for each correct answer and $2$ marks been deducted for each incorrect answer, then Yash would have scored $50$ marks. How many questions were there in the test?
\item Places $A$ and $B$ are $100km$ apart on a highway. One car starts from $A$ and another from $B$ at the same time. If the car travel in the same direction at different speeds, they meet in $5$hrs. If they travel towards each other, they meet in $1$hr. What are the speeds of the two cars?
\item The area of rectangle gets reduced by $9$ square units, if its length is reduced by $5$ units and breadth is increased by $3$ units. If we increase the length by $3$ units and the breadth by $2$ units, the area increases by $67$ square units. Find the dimensions of the rectangle.
\item Narayan tells his daughter, `Seven years ago, I was seven times as old as you were then. Also, $3$ years from now, I shall be $3$ times as old as  you will be.' Find their ages. 
\item The coach of a cricket team buys $3$ bats and $6$ balls for $Rs.3900$. Later, she buys another bat and $3$ more balls of the same kind for $Rs.3300$. Find the cost of a bat and ball.
\item The cost of $2kg$ of apples and $1kg$ of grapes on a day was found to be $Rs.160$. After a month, the cost of $4kg$ of apples and $2kg$ of grapes is $Rs.300$. Assuming that the costs remain unchanged, find the cost of a kg of apples and grapes. 
\item Draw the graphs of the equations $x-y+1=0$ and $3x+2y-12=0$. Determine the coordinates of the vertices of the triangle formed by these lines and the axis and shade the triangular region.
\end{enumerate}
