\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
	\item 		Find the values of $x$ and $y$ so that the vectors
$2\hat{i}+3\hat{j}$
and 
$x\hat{i}+y\hat{j}$
are equal.
\\
\solution
\input{chapters/12/10/2/4/vector.tex}
\item Find the values of $x, y, z$ so that the vectors 
$x\hat{i}+2\hat{j}+z\hat{k}$
and 
$2\hat{i}+y\hat{j}+\hat{k}$
are equal.
\item Find the sum of the vectors $\vec{a}=\hat{i}-2\hat{j}+\hat{k}$,  $\vec{b}=-2\hat{i}+4\hat{j}+5\hat{k}$ and $\vec{c}=\hat{i}-6\hat{j}-7\hat{k}$.
\item Find the slope of a line,  which passes through the origin and the mid point of the line segment joining the points $\vec{P}$(0, -4) and $\vec{B}$(8, 0).
\label{chapters/11/10/1/5}
	\\
	\solution
\input{chapters/11/10/1/5/matrix.tex}
\item Find the angle between x-axis and the line joining points (3, -1) and (4, -2).
\label{chapters/11/10/1/10}
\\
\solution 
\input{chapters/11/10/1/10/matrix.tex}
\item A line passes through $\vec{A}(x_1, y_1)$ and $\vec{B}(h, k)$. If slope of the line is m,  show that $(k-y_1)=m(h-x_1)$.
\label{chapters/11/10/1/12}
\\
\solution 
\input{chapters/11/10/1/12/matrix.tex}
\item
Show that the line through the points \brak{4, 7, 8}, \brak{2, 3, 4} is parallel to the line through the points \brak{-1, -2, 1}, \brak{1, 2, 5}.
	\label{12.11.2.3}
\\
\solution
	\input {chapters/12/11/2/3/vec2.tex}
\item The vector having intial and terminal points as (-2, 5, 0) and (3, 7, 4), respectively is
\solution
The desired vector is
\begin{align}
	\myvec{3 \\ 7 \\ 4}
	-\myvec{-2 \\ 5 \\ 0} = 
	\myvec{5 \\ 2 \\ 4}  
\end{align}
\item Find the vector joining the points $\vec{P}\brak{2, 3, 0}$ and $\vec{Q}\brak{-1, -2, -4}$ directed from $\vec{P}$ to $\vec{Q}$.
\item Without using distance formula,  show that points $\vec{A}(– 2,  – 1),  \vec{B}(4,  0),  \vec{C}(3,  3)$ and $\vec{D}(–3,  2)$ are the vertices of a parallelogram.
\label{chapters/11/10/1/9}
\\
\solution
\input{chapters/11/10/1/9/vector.tex}
\item If the points $\vec{A}(6,  1),  \vec{B}(8,  2),  \vec{C}(9,  4)$ and $\vec{D}(p,  3)$ are the vertices of a parallelogram,  taken in order,  find the value of $p$.
\label{10/7/0/10}
\item 
If $(1,  2),  (4,  y),  (x,  6)$ and $(3,  5)$ are the vertices of a parallelogram taken in order,  find $x$ and $y$.
\label{10/7/2/6}
\item The fourth vertex $\vec{D}$ of a parallelogram $ABCD$ whose three vertices are
	$\vec{A} (–2,  3),  \vec{B} (6,  7)$ and  $\vec{C} (8,  3)$ is
\item Verify if the points $\vec{A}(4, 3),  \vec{B}(6, 4), \vec{C}(5, -6)$  and  $\vec{D}(-3, 5)$ are the vertices of a parallelogram.
\item A girl walks 4 km towards west,  then she walks 3 km in a direction 30$^{\circ}$ east of north and stops. Determine the girl's displacement from her initial point of departure.\\
	\solution
		\input{chapters/12/10/5/3/vec.tex}
\item $(-1, 2, 1),  (1, -2, 5),  (4, -7, 8)$ and $(2, -3, 4)$ are the vertices of a parallelogram.
\item Three vertices of a parallelogram $ABCD$ are $\vec{A}(3, -1, 2),  \vec{B}(1, -2, 4)$ and $\vec{C}(-1, 1, 2)$. Find the coordinates of the fourth vertex.
\item If the origin is the centroid of the triangle $PQR$ with vertices $\vec{P}(2a, 2, 6),  \vec{Q}(-4, 3b, -10)$ and $R(8, 14, 2c)$,  then find the values of $a,  b$ and $c$.
\item Find the slope of lines
\begin{enumerate}
\item  Passing through the points $(3, -2)$ and $(-1, 4)$
\item  Passing through the points $(3, -2)$ and $(7, -2)$
\item  passing through the points $(3, -2)$ and $(3, 4)$	
\item  Making inclination of $60\degree$ with the positive direction of x-axis.
\end{enumerate}
\item The centroid of a triangle $ABC$ is at the point $(1, 1, 1)$. If the coordinates of $\vec{A}$ and $\vec{B}$ are $(3, -5, 7)$ and $(-1, 7, -6)$,  respectively find the coordinates of the point $\vec{C}$.
\item Represent graphically a displacement of $40$ km,  $30\degree$ west of south.
	\item Rain is falling vertically with a speed of 35 $m s^{-1}$
. Winds starts blowing after sometime with a speed of 12 $m s^{-1}$ in
east to west direction. In which direction should a boy waiting at a bus stop hold his umbrella ?
%
\item A motorboat is racing towards north at 25 km/h and the water current in that region is 10 km/h in the direction of 60$\degree$ east of south. Find the resultant velocity of the boat.
\item Rain is falling vertically with a speed of 35 $m s^{-1}$
. A woman rides a bicycle with a speed of 12 $ms^{-1}$ in east to west
direction. What is the direction in which she should hold her umbrella ?
\item Rain is falling vertically with a speed of 30 $m s^{-1}$. A woman rides a bicycle with a speed  of 10 $m s^{-1}$ in the north to south direction. What is the direction in which she should
hold her umbrella?
\item A man can swim with a speed of 4.0 km/h in still water. How long does he take to cross a river 1.0 km wide if the river flows steadily at 3.0 km/h and he makes his strokes normal to the river current? How far down the river does he go when he reaches the other bank ?
\item In a harbour,  wind is blowing at the speed of 72 km/h and the flag on the mast of a boat anchored in the harbour flutters along the N-E direction. If the boat starts moving at a speed of 51 km/h to the north,  what is the direction of the flag on the mast of the boat ?
\item In which quadrant or on which axis do each of the points (-2, 4), (3, -1), (-1, 0), (1, 2) and (-3, -5) lie? Verify your answer by locating them on the Cartesian plane.
\item Plot the points $(x, y)$ given in 
\tabref{table:Table of values}.
\begin{table}[H]
	\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline	
x & -2 & -1 & 0 & 1 & 3\\
\hline
y & 8 & 7 & -1.25 & 3 & -1\\
\hline
\end{tabular}
\caption{}
\label{table:Table of values}
\end{table}
\end{enumerate}
