\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item
Find the angle between the lines whose direction ratios are $a,b,c$ and $b-c,c-a,a-b$.
\\
\solution
\input{chapters/12/11/4/3/vec4.tex}
\item Name the type of quadrilateral formed, if any, by the following points,and give reasons for your answer
\begin{enumerate}
\item $A(-1,-2), B(1,0), (C-1,2), D(-3,0)$
\item $A(-3,5), B(-3,1), C(0,3), D(-1,-4)$
\item $A(4,5), B(7,6), C(4,3), D(1,2)$
\end{enumerate}
\solution
		\input{chapters/10/7/1/6/inner.tex}
\item Find the projection of the vector $\hat{i}+3\hat{j}+7\hat{k}$ on the vector $7\hat{i}-\hat{j}+8\hat{k}$.
	\\
	\solution
		\input{chapters/12/10/3/4/inner.tex}
\item Find the projection of the vector $\hat{i}-\hat{j}$ on the vector $\hat{i}+\hat{j}$.
	\\
\solution
		\input{chapters/12/10/3/3/inner.tex}
\item Show that each of the given three vectors is a unit vector: 
 $\frac{1}{7}(2\hat{i}+3\hat{j}+6\hat{k}),\frac{1}{7}(3\hat{i}-6\hat{j}+2\hat{k}),\frac{1}{7}(6\hat{i}+2\hat{j}-3\hat{k}$).
Also,show that they are mutually perpendicular to each other.
	\\
	\solution
		\input{chapters/12/10/3/5/inner.tex}
\item If $\overrightarrow {a}=2\hat{i}+2\hat{j}3\hat{k},\overrightarrow {b}=\hat{-i}+2\hat{j}+\hat{k}$ and $\overrightarrow {c}=3\hat{i}+\hat{j}$ are such that $\overrightarrow {a}+\lambda\overrightarrow {b}$ is perpendicular to $\overrightarrow {c}$,then find the value of $\lambda$.
	\\
		\input{chapters/12/10/3/10/inner.tex}
\item Show that $\abs {\overrightarrow {a}}\overrightarrow {b}+\abs{\overrightarrow {b}}\overrightarrow {a}$ is perpendicular to $\abs{\overrightarrow {a}} \overrightarrow {b}-\abs{\overrightarrow {b}} \overrightarrow {a}$, for any two nonzero vectors $\overrightarrow {a}$ and $\overrightarrow {b}$.
	\\
	\solution
		\input{chapters/12/10/3/11/inner.tex}
\item If $\overrightarrow {a},\overrightarrow {b},\overrightarrow {c}$ are unit vectors such that $\overrightarrow {a}+\overrightarrow {b}+\overrightarrow {c}=\overrightarrow {0}$, find the value of $\overrightarrow {a}.\overrightarrow {b}+\overrightarrow {b}.\overrightarrow {c}+\overrightarrow {c}.\overrightarrow {a}$.
	\\
	\solution
		\input{chapters/12/10/3/13/norm.tex}
\item If either vector $\overrightarrow {a}=0$ or $\overrightarrow {b}=0$, then $\overrightarrow {a}.\overrightarrow {b}$=0. But the converse need not be true. Justify your answer with an example.
	\\
	\solution
		\input{chapters/12/10/3/14/inner.tex}
\item Show that the vectors $2\hat{i}-\hat{j}+\hat{k},\hat{i}-3\hat{j}-5\hat{k}$ and  $3\hat{i}-4\hat{j}-4\hat{k}$ from the vertices of a right angled triangle.
	\\
	\solution
		\input{chapters/12/10/3/17/inner.tex}
\item Show that the points A, B and C with position vectors, $3\hat{i}-4\hat{j}-4\hat{k}, 2\hat{i}-\hat{j}+\hat{k}$ and $\hat{i}-3\hat{j}-5\hat{k}$, respectively, form the vertices of a right angled
triangle.
\\
\solution
		\input{chapters/12/10/2/17/inner.tex}
\item Let $\vec{a}=\hat{i}+4\hat{j}+2\hat{k}, \vec{b}=3\hat{i}-2\hat{j}+7\hat{k}$ and $\vec{c}=2\hat{i}-\hat{j}+4\hat{k}$. Find a vector $\vec{d}$ which is perpendicular to both $\vec{a}$ and $\vec{b}$, and $\vec{c}\cdot \vec{d}$=15.\\
	\solution
		\input{chapters/12/10/5/12/equation.tex}
\item Prove that $(\vec{a}+\vec{b})\cdot(\vec{a}+\vec{b})=|{\vec{a}}|^2+|{\vec{b}}|^2$, if and only if $\vec{a}, \vec{b}$ are perpendicular, given $\vec{a}\neq\vec{0}, \vec{b}\neq\vec{0}$.\\
	\solution
		\input{chapters/12/10/5/15/inner.tex}
\item $ABCD$ is a rectangle formed by the points $\vec{A}(–1, –1), \vec{B}(– 1, 4), \vec{C}(5, 4)$  and  $\vec{D}(5, – 1)$. $\vec{P}, \vec{Q}, \vec{R}$ and $\vec{S}$ are the mid-points of $AB, BC, CD$ and $DA$ respectively. Is the quadrilateral $PQRS$ a square? a rectangle? or a rhombus? Justify your answer.
	\\
	\input{chapters/10/7/4/8/inner.tex}
\item Without using the Baudhayana theorem, show that the points $A(4,4), B(3,5)$ and $C(-1,-1)$ are the vertices of a right angled triangle.
\label{chapters/11/10/1/6}
\input{chapters/11/10/1/6/matrix.tex}
\item The line through the points $(h, 3)$ and $(4, 1)$ intersects the line $7x- 9y- 19= 0$ at a right angle. Find the value of $h$.
\label{chapters/11/10/3/10}
\\
\solution
\input{chapters/11/10/3/10/line.tex}
\item In the following cases, determine whether the given planes are parallel or perpendicular, and in case they are neither, find the angles between them.
\begin{enumerate}
\item $7x + 5y + 6z + 30 = 0$ and $3x – y – 10z + 4 = 0$
\item $2x + y + 3z – 2 = 0$ and $x – 2y + 5 = 0$
\item $2x – 2y + 4z + 5 = 0$ and $3x – 3y + 6z – 1 = 0$
\item $2x – y + 3z – 1 = 0$ and $2x – y + 3z + 3 = 0$
\item $4x + 8y + z – 8 = 0$ and $y + z – 4 = 0$
\end{enumerate}
    \solution
		\input{chapters/12/11/3/13/inner.tex}
		\item 
 Show that the line joining the origin to the point $P(2, 1, 1)$ is perpendicular to the
line determined by the points $A(3, 5, – 1), B(4, 3, – 1)$.
\\
    \solution
		\input{chapters/12/11/4/1/inner.tex}
	\item  If $l_1, m_1,n_1 \text{ and } l_2,m_2,n_2$ are the direction cosines of two mutually perpendicular lines, show that the direction cosines of the line perpendicular to both these are  $m_1n_2-m_2n_1,n_1l_2-n_2l_1,l_1m_2-l_2m_1$.
\\
    \solution
		\input{chapters/12/11/4/2/inner.tex}
	\item If the lines $\frac{x-1}{-3} = \frac{y-2}{2k} = \frac{z-3}{2}$ and  $\frac{x-1}{3k} = \frac{y-1}{1} = \frac{z-6}{-5}$ are perpendicular, find the value of $k$.\\
    \solution
		\input{chapters/12/11/4/6/inner.tex}
\item If $\vec{a},\vec{b},\vec{c}$ are mutually perpendicular vectors of equal magnitudes, show that the vector $\vec{c}\cdot\vec{d}$=15 is equally inclined to $\vec{a},\vec{b}$ and $\vec{c}$.
    \item If $ \vec{A},\vec{B},\vec{C} $ are mutually perpendicular vectors of equal magnitudes,show that the  $ \vec{A}+\vec{B}+\vec{C} $ is equally inclined to $ \vec{A},\vec{B}  \text{ and }  \vec{C} $.
\item Check whether $(5,-2), (6,4)$ and $(7,-2)$ are the vertices of an isosceles triangle.
\item The perpendicular bisector of the line segment joining the points $\vec{A} (1, 5) \text{ and }
\vec{B} (4, 6)$ cuts the y-axis at
\begin{enumerate}
	\item$(0, 13)$ 
	\item $(0, –13)$
	\item$(0, 12) $
	\item$(13, 0)$
\end{enumerate}
\item The point which lies on the perpendicular bisector of the line segment joining the
	points $\vec{A} (–2, –5)\text { and } \vec{B} (2, 5) $ is
\begin{enumerate}
\item  	$(0, 0)$
\item  $(0, 2)$ 
\item  $(2, 0)$ 
\item  $(–2, 0)$
\end{enumerate}
\item The points $ (–4, 0), (4, 0), (0, 3) $ are the vertices of
	\begin{enumerate}
\item right triangle 
\item isosceles triangle
\item  equilateral triangle
\item  scalene triangle 
\end{enumerate}
\item The point $\vec{A}(2,7)$ lies on the perpendicular bisector of line segment joining the points $\vec{P}(6,5)\text{ and } \vec{Q}(0,-4)$.
\item The points $\vec{A}(-1,-2), \vec{B}(4,3), \vec{C}(2,5) \text{ and } \vec{D}(-3,0)$ in that order form a rectangle.
\item Name the type of triangle formed by the points $\vec{A}(-5,6),\vec{B}(-4,-2),\text{ and }\vec{C}(7,5)$.
\item What type of a quadrilateral do the points $\vec{A}(2,-2),\vec{B}(7,3),\vec{C}(11,-1),\text{ and }\vec{D}(6,-6)$ taken in that order, form?
\item Find the coordinates of the point $\vec{Q}$ on the $x$-axis which lies on the perpendicular bisector of the line segment joining the points $\vec{A}(-5,-2) \text{ and } \vec{B}(4,-2)$. Name the type of triangle formed by points $\vec{Q},\vec{A}\text{ and }\vec{B}$.
\item The points $\vec{A}(2,9),\vec{B}(a,5) \text{ and }\vec{C}(5,5)$ are the vertices of a triangle $\vec{ABC}$ right angled at $\vec{B}$. Find the values of a and hence the area of $\triangle \vec{ABC}$.
\item Find a vector of magnitude 6, which is perpendicular to both the vectors $2\hat{i}-\hat{j}$+$2\hat{k}\text{ and }4\hat{i}-\hat{j}+3\hat{k}$.
\item If A,B,C,D  are the points with position vectors $\hat{i}+\hat{j}-\hat{k}$, $2\hat{i}-\hat{j}+3\hat{k}$, $2\hat{i}-3\hat{k}$, $3\hat{i}$-$2\hat{j}$+$\hat{k}$, respectively, find the projection of $\overline{AB}$ $\text{ along }$ $\overline{CD}$.
\item Find the value of $\lambda$ such that the vectors $\vec{a}=2\hat{i}+\lambda\hat{j}+\hat{k}$ $\text{and}$ $\vec{b}=\hat{i}+2\hat{j}+3\hat{k}$ are orthogonal.
	\begin{enumerate}
\item 0
\item 1 
\item $\frac{3}{2}$
\item $-\frac{5}{2}$
	\end{enumerate}
\item Projection vector of $\vec{a}$ on $\vec{b}$ is
	\begin{enumerate}
\item $\left(\dfrac{\vec{a}\cdot\vec{b}}{\abs{\vec{b}}^2}\right)$
\item $\frac{\vec{a}\cdot\vec{b}}{\abs{\vec{b}}}$
\item $\frac{\vec{a}\cdot\vec{b}}{\abs{\vec{a}}}$
\item $\left(\dfrac{\vec{a}\cdot\vec{b}}{\abs{\vec{a}}^2}\right)$
\end{enumerate}
\item The vectors $\lambda\hat{i}+\lambda\hat{j}+2\hat{k}$, $\hat{i}+\lambda\hat{j}-\hat{k}$ $\text{ and }$ $2\hat{i}-\hat{j}+\lambda\hat{k}$ are coplanar if
	\begin{enumerate}
\item	$\lambda=-2$
\item $\lambda=0$
\item $\lambda=1$
\item	$\lambda=-1$
\end{enumerate}
\item The number of vectors of unit length perpendicular to the vectors $\vec{a}=2\hat{i}+\hat{j}+2\hat{k}$ $\text{ and }$ $\vec{b}=\hat{j}+\hat{k}$ is
	\begin{enumerate}
\item one
\item  two
\item three
\item infinite
\end{enumerate}
\item If $\vec{r}\cdot\vec{a}=0, \vec{r}\cdot\vec{b}=0$ and $\vec{r}\cdot\vec{c}=0$ for some non-zero vector $\vec{r}$, then the value of $\vec{a}\cdot(\vec{b}\times\vec{c})$ is \rule{1cm}{0.15mm}.
\item If $\abs{\vec{a}+\vec{b}}$ = $\abs{\vec{a}-\vec{b}}$, then the vectors $\vec{a}$ $\text {and}$ $\vec{b}$ are orthogonal.
\item Prove that the lines $x=py+q , z=ry+s \text{ and } x=p^{\prime}y+q^{\prime}, z=r^{\prime}y+s^{\prime} $ are perpendicular if $pp^{\prime}+rr^{\prime}+1=0$.
\item Find the equation of a plane which  bisects perpendicularly the line joining the points A$(2,3,4)$ and B$(4,5,8)$ at right angles.
\item $\overrightarrow{AB}=3\hat{i}-\hat{j}+\hat{k}$ and $\overrightarrow{CD}=-3\hat{i}+2\hat{j}+4\hat{k}$ are two vectors. The position vectors of the points A and C are $6\hat{i}+7\hat{j}+4\hat{k}$ and $-9\hat{j}+2\hat{k},$ respectively. Find the position vector of a point P on the line AB and a point Q on the line CD such that $\overrightarrow{PQ}$ is perpendicular to $\overrightarrow{AB}$ and $\overrightarrow{CD}$ both.
\item Show that the straight lines whose direction cosines are given by $2l+2m-n=0$ and $mn+nl+lm=0$ are at right angles.
\item If $l_1, m_1, n_1;l_2, m_2, n_2;l_3, m_3, n_3$ are the direction cosines of the three mutually perpendcular lines, prove that the line whose direction cosines are propotional to $l_1+l_2+l_3 , m_1+m_2,m_3, n_1+n_2+n_3$ make angles with them.
\item The intercepts made by the plane $2x-3y+5z+4=0$ on the co-ordinate axis are $\brak{-2,\dfrac{4}{3},-\dfrac{4}{5}}$.
\item The line $\overrightarrow{r}=2\hat{i}-3\hat{j}-\hat{k}+\lambda(\hat{i}-\hat{j}+2\hat{k})$ lies in the plane $\overrightarrow{r} \cdot (3\hat{i}+\hat{j}-\hat{k})+2=0$.
\item Line joining the points (3,-4) and (-2,6) is perpendicular to the line joining the points (-3,6) and (9,-18).
\end{enumerate}
