\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item Find the angle between two vectors $\overrightarrow{a}$ and $\overrightarrow {b} $ with magnitudes $\sqrt{3}$ and 2 respectively having $\overrightarrow {a}\cdot\overrightarrow {b}=\sqrt{6}$.
		\label{prob:12/10/3/1/inner}
	\\
	\solution
		\input{chapters/12/10/3/1/inner.tex}
\item Find the angle between the the vectors $\hat{i}-2\hat{j}+3\hat{k}$ and $3\hat{i}-2\hat{j}+\hat{k}$.
	\\
	\solution
		\input{chapters/12/10/3/2/inner.tex}
\item Evaluate the product $(3\overrightarrow {a}-5\overrightarrow {b})\cdot (2\overrightarrow {a}+7\overrightarrow {b})$.
	\\
	\solution
		\input{chapters/12/10/3/7/inner.tex}
\item If the vertices $\vec{A}, \vec{B}, \vec{C}$ of a triangle $ABC$ are (1, 2, 3),  (-1, 0, 0),  (0, 1, 2),  respectively,  then find  $\angle{ABC}$.
	\\
	\solution
		\input{chapters/12/10/3/15/inner.tex}
	\item The slope of a line is double of the slope of another line. If tangent of the angle between them is 1/3,  find the slopes of the lines.
\label{chapters/11/10/1/11}
\\
\solution 
\input{chapters/11/10/1/11/matrix.tex}
\item    Find angle between the lines,  $\sqrt{3}x+y=1$ and $x+\sqrt{3}y$=1.
\label{chapters/11/10/3/9}
\\
   \solution 
\input{chapters/11/10/3/9/line.tex}
\item Find the angle between the vectors $2\hat{i}-\hat{j}+\hat{k}$ and $3\hat{i}+4\hat{j}-\hat{k}$.
\item The angles between two vectors $\vec{a},  \vec{b}$ with magnitude $\sqrt{3},  4$ respectively,  and $\vec{a} \cdot \vec{b}= 2\sqrt{3}$ is
\item Find the angle between the lines 
\begin{align}
	\overrightarrow{r}&=3\hat{i}-2\hat{j}+6\hat{k}+\lambda(2\hat{i}+\hat{j}+2\hat{k})
	\text{ and}
	\\
	\overrightarrow{r}&=(2\hat{j}-5\hat{k})+\mu(6\hat{i}+3\hat{j}+2\hat{k})
\end{align}
%
\solution  The given lines can be expressed  in the form 
of 
	\eqref{eq:param-form}
	as
\begin{align}
	\vec{x} = \myvec{3 \\ -2 \\ 6} + \kappa_1 \myvec{2 \\ 1 \\ 2}
	\\
	\vec{x} = \myvec{0 \\ 2 \\ -5 } + \kappa_2 \myvec{6 \\ 3 \\ 2}
\end{align}
From the above,  it is obvious that the direction vectors of the two lines are
\begin{align}
\vec{m}_1 =\myvec{2 \\ 1 \\ 2}, \
	\vec{m}_2=\myvec{6 \\ 3 \\ 2}
\end{align}
	From \eqref{eq:angle-inner},  the angle between the two lines is  obtained as
\begin{align}
	\cos \theta = \frac{19}{21}
\end{align}
\item The vectors $\vec{a}=3\hat{i}-2\hat{j}+2\hat{k}$ $\text{ and }$ $\vec{b}=\hat{i}-2\hat{k}$ are the adjancent sides of a parallelogram. The acute angle between its diagonals is \rule{1cm}{0.15mm}.
\item The sine of the angle between the straight line 
\begin{align}
	\frac{x-2}{3}=\frac{y-3}{4}=\frac{z-4}{5} 
\end{align}
and the plane  
\begin{align}
2x-2y+z=5
\end{align}
is
\solution The given line can be expressed in the form 
	\eqref{eq:param-form}
	as
\begin{align}
	\vec{x} = \myvec{2 \\ 3 \\ 4} + \kappa_1 \myvec{3 \\ 4 \\ 5}
\end{align}
Hence the direction vector of this line is 
\begin{align}
\myvec{3 \\ 4 \\ 5}
\end{align}
	From \eqref{eq:normal-form},  the normal vector of the given plane is 
\begin{align}
\myvec{2 \\ -2 \\ 1}
\end{align}
Thus,  the cosine of the angle between the two is 
obtained from \eqref{eq:angle-inner} as
\begin{align}
	\frac{\sqrt{2}}{10}, 
\end{align}
which is sine of the angle between the plane and the line.
\item The plane $2x-3y+6z-11=0$ makes an angle $\sin^{-1}(\alpha)$ with x-axis. The value of $\alpha$ is equal to 
\item Find the angle between the vectors $2\hat{i}-\hat{j}+\hat{k}$ $\text{and}$ $3\hat{i}+4\hat{j}-\hat{k}$.
\item The angles between two vectors $\vec{a}$ $\text{and}$ $\vec{b}$ with magnitude $\sqrt{3}$ $\text{ and }$ 4,  respectively,  and $\vec{a}$,  $\vec{b}$= $2\sqrt{3}$ is
\item The angle between the line 
\begin{align}
	\overrightarrow{r}=(5\hat{i}-\hat{j}-4\hat{k})+\lambda(2\hat{i}-\hat{j}+\hat{k})
\end{align}
	and the plane 
\begin{align}
	\overrightarrow{r} \cdot (3\hat{i}-4\hat{j}-\hat{k})+5=0
\end{align}
	is $\sin^{-1}\brak{\frac{5}{2\sqrt{91}}}$.
\item The angle between the planes 
\begin{align}
	\overrightarrow{r} \cdot (2\hat{i}-3\hat{j}+\hat{k})&=1 
	\text{ and }
	\\
	\overrightarrow{r} \cdot (\hat{i}-\hat{j})&=4  
\end{align}
is
	$\cos^{-1} \brak{\frac{-5}{\sqrt{58}}}$.
\item Find the angle between the lines 
\begin{align}
	y&=(2-\sqrt{3})(x+5)\text{ and }
	\\
	y&=(2+\sqrt{3})(x-7).
\end{align}
\item The unit vector normal to the plane $x+2y+3z-6=0$ is $\frac{1}{\sqrt{14}}\hat{i} + \frac{2}{\sqrt{14}}\hat{j} + \frac{3}{\sqrt{14}}\hat{k}$.
\item The scalar product of the vector $\hat{i}+\hat{j}+\hat{k}$ with a unit vector along the sum of vectors $2\hat{i}+4\hat{j}-5\hat{k}$ and $\lambda\hat{i}+2\hat{j}+3\hat{k}$ is equal to one. Find the value of $\lambda$.
\item  Find the angle between the following pairs of lines.
\begin{enumerate}	
\item  
\begin{align}
\overrightarrow{r}=2\hat{i}-5\hat{j}+\hat{k}+\lambda(3\hat{i}+2\hat{j}+6\hat{k}) \text{ and }\\ \overrightarrow{r}=7\hat{i}-6\hat{k}+\mu(\hat{i}+2\hat{j}+2\hat{k}) 
\end{align} 
\item 
\begin{align}
\overrightarrow{r}=3\hat{i}+\hat{j}-2\hat{k}+\lambda(\hat{i}-\hat{j}-2\hat{k}) \text{ and }\\ \overrightarrow{r}=2\hat{i}-\hat{j}-56\hat{k}+\mu(3\hat{i}-5\hat{j}-4\hat{k})
\end{align}
\item 
\begin{align} \frac{x-2}{2}=\frac{y-1}{5}=\frac{z+3}{-3}\text{ and } \frac{x+2}{-1}=\frac{y-4}{8}=\frac{z-5}{4}.
\end{align}
\item
\begin{align} \frac{x}{2}=\frac{y}{2}=\frac{z}{1}\text{ and } \frac{x-5}{4}=\frac{y-2}{1}=\frac{z-3}{8}.
\end{align}
\end{enumerate}
\item If the co-ordinates of the points $\vec{A}, \vec{B}, \vec{C}, \vec{D}$ be $(1, 2, 3)$,  $(4, 5, 7)$,  $(-4, 3, -6)$ and $(2, 9, 2)$ respectively,  then find the angle between the lines $AB$ and $CD$.
\item If the angle between two lines is $\frac{\pi}{4}$ and slope of one of the lines is $\frac{1}{2}$, find the slope of the other line.
\item Find the angle between two vectors $\overrightarrow{a}$ and $\overrightarrow{b}$ with magnitudes $1$ and $2$ respectively and when $\overrightarrow{a}\cdot \overrightarrow{b} = 1$.
\item Find angle $\theta$ between the vectors $\overrightarrow{a} = \hat{i} +\hat{j} -\hat{k}$ and $\overrightarrow{b} = \hat{i} -\hat{j}+\hat{k}$.
\item If $\hat{i}+\hat{j}+\hat{k}, 2\hat{i}+5\hat{j}, 3\hat{i}+2\hat{j}-3\hat{k}$ and $\hat{i}-6\hat{j}-\hat{k}$ are the position vectors of points $\vec{A}, \vec{B}, \vec{C}$ and $\vec{D}$ respectively, then find the angle between $\overrightarrow{AB}$ and $\overrightarrow{CD}$. Deduce that $\overrightarrow{AB}$ and $\overrightarrow{CD}$ are collinear.
\item Find the angle between the pair of lines given by
\begin{align}
\overrightarrow{r}= 3 \hat{i}+ 2 \hat{j}- 4 \hat{k}+ \lambda(\hat{i}+ 2 \hat{j}+ 2 \hat{k}) \\
\text{ and } \overrightarrow{r}= 5 \hat{i}+ 2 \hat{j}+ \mu(3 \hat{i}+ 2 \hat{j}+ 6 \hat{k}) 
\end{align}
\item Find the angle between the pair of lines:
\begin{align}
\frac{x+3}{3}= \frac{y-1}{5}= \frac{z+3}{4}\\
\text{ and }\frac{x+1}{1}= \frac{y-4}{1}= \frac{z+5}{2}
\end{align}
\item Find the angle between the two planes $2x +y -2z =5$ and $3x- 6y- 2z= 7$ using vector method.
\item Find the angle between the two planes $3x -6y +2z =7$ and $2x +2y -2z =5$.
\item Find the angle between the line $\frac{x+1}{2} =\frac{y}{3} =\frac{z-3}{6}$ and the plane $10x +2y -11z =3$.
\end{enumerate}
