\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item Show that the plane $x - 5y - 2z = 1$ contains the line $\frac{x - 5}{3}$ = y = $2 -z$.
\hfill (12, 2020)
    \item If the equation of a line is
    \begin{align*}
        x &= ay + b, \\
        z &= cy + d,
    \end{align*}
    then find its parametric form.
    \hfill (12, 2023)
    \item Equation of the line passing through the origin and making $30\degree$, $60\degree$, and $90\degree$ with the $X, Y, Z$ axes respectively is
    \hfill (12, 2023)
	\item A line passes through the point with position vector $2\hat{i} - \hat{j} + 4\hat{k}$ and is in the direction of the vector $\hat{i} + \hat{j} - 2\hat{k}$. Find the equation of the line. \hfill (12, 2019)
	\item Find the equation of the plane passing through the points having position vectors $\hat{i} + \hat{j} - 2\hat{k}$, $2\hat{i} - \hat{j} + \hat{k}$, and $\hat{i} + 2\hat{j} + \hat{k}$. (12, 2019)
	\item Find the equation of the plane passing through the points $\vec{A}(2, 5, -3)$, $\vec{B}(-2, -3, 5)$ and $\vec{C}(5, 3, -3)$. \hfill (12, 2019)
	\item Find the value of $x$ such that the four points with position vectors $\vec{A}(3\hat{i} + 2\hat{j} + \hat{k})$, $\vec{B}(4\hat{i} + x\hat{j} + 5\hat{k})$, $\vec{C}(4\hat{i} + 2\hat{j} - 2\hat{k})$, and $\vec{D}(6\hat{i} + 5\hat{j} - \hat{k})$ are coplanar. \hfill (12, 2019)
	\item Find the value of $x$ such that the four points $\vec{A}(x, 5, -1)$, $\vec{B}(3, 2, 1)$, $\vec{C}(4, 5, 5)$, and $\vec{D}(4, 2, -2)$ are coplanar. \hfill (12, 2019)
\item Find the value of $a$ so that the point $(3, a)$ lies on the line represented by $2x - 3y = 5$. \hfill (10, 2019)
\item Point $\vec{P}$ divides the line segment joining the points $\vec{A}(2, 1)$ and $\vec{B}(5, -8)$ such that $\frac{AP}{AB} = \frac{1}{3}$. If $\vec{P}$ lies on the line $2x - y + k = 0$, find the value of $k$. \hfill (10, 2019)
    \item The line segment joining the points $\vec{A}(2,1)$ and $\vec{B}(5,-8)$ is trisected at the points $\vec{P}$ and $\vec{Q}$, where $\vec{P}$ is nearer to $\vec{A}$. If $\vec{P}$ lies on the line $2x - y + k = 0$, find the value of $k$. \hfill (10, 2018)
\item Find the  equation of the plane passing through the points $\brak{2,5,-3},\brak{-2,-3,5}$ and $\brak{5,3,-3}$. Also find the point of intersection of this plane with the line passing through points $\brak{3,1,5}$ and $\brak{-1,-3,-1}$.
\hfill (12, 2018)
\item A line passes through the point with position vector $2\hat{i}-\hat{j}+4\hat{k}$ and is in the direction of the vector $\hat{i}+\hat{j}-2\hat{k}$. Find the equation of the line. 
\hfill (12, 2018) 
    \item Find the value of $\lambda$, if four points with position vectors $\vec{P}_1 = 3\hat{i} + 6\hat{j} + 9\hat{k}$, $\vec{P}_2 = \hat{i} + 2\hat{j} + 3\hat{k}$, $\vec{P}_3 = 2\hat{i} + 3\hat{j} + \hat{k}$, and $\vec{P}_4 = 4\hat{i} + 6\hat{j} + \lambda\hat{k}$ are coplanar. \hfill (12, 2017)
\item Write the sum of intercepts cut off by the plane $\overrightarrow{r}.\myvec{2\hat{i}+\hat{j}-\hat{k}} - 5 = 0$ on the three axes. 

	\hfill (12, 2016)
\item Find the equation of the plane with intercepts $3,-4$ and $2$ on the three axes.

	\hfill (12, 2016)
\item A point $\vec{P}$ divides the line segment joining the points $\vec{A}\brak{3,-5}$ and $\vec{B}\brak{-4,8}$ such that $\frac{AP}{PB} = \frac{K}{1}$. If $\vec{P}$ lies on the line $x + y = 0$, then find the value of $K$. 
\hfill (10, 2012)
\item If the point $\vec{A}\brak{x,y}$, $\vec{B}\brak{3,6}$ and $\vec{C}\brak{-3,4}$ are collinear, show that $x - 3y + 15 = 0$. 

\hfill (10, 2012)
\item \textbf{Assertion (A):} Point $\vec{P}$(0,2) is the point of intersection of $Y$ axis with  the line $3x+2y=4$.\\
    \textbf{Reason (R):} The distance of point $\vec{P}$(0,2) from $X$ axis is 2 units. \hfill (10, 2023)
  \item The pair of linear equations $2x=5y+6$ and $15y=6x-18$ represents two lines which are:
      \begin{enumerate}
        \item intersecting
        \item parallel
        \item coincident
        \item either intersecting or parallel
      \end{enumerate} \hfill (10, 2023)
\item Write the equation of the line PQ passing through points $\vec{P}(2,2,1)$ and $\vec{Q}(5,1,-2)$. Hence, find the $y$-coordinate of the point on the line PQ whose $z$-coordinate is -2.

	\hfill (12, 2022)
\item Find the equation of a plane which passes through the point $(3,2,0)$ and contains the line $\frac{x-3}{1}=\frac{y-6}{5}=\frac{z-4}{4}$. \hfill (12, 2022)
\item If the graph of a pair of lines $ x - 2y + 3 = 0 $ and $ 2x - 4y = 5 $ be drawn, that what type of lines are drawn ? \hfill (10, 2021)
\item If segment of the line intercepted between the co-ordinate-axes is bisected
at the point $\vec{M}\brak{2, 3}$, then the equation of this line is
\hfill (12, 2021)
\item The equation of a line through $(2,-4)$ and parallel to $X$ axis is \underline{\hspace{2cm}}. 

	\hfill (12, 2021)

\item Find the equation of the median through vertex $\vec{A}$ of the triangle $ABC$, having vertices $\vec{A}\brak{2,5}$, $\vec{B}\brak{-4,9}$ and $\vec{C}\brak{-2, -1}$. \hfill (12, 2021)
\item Find the value of $x$ such that the points $\vec{A}\brak{3,2,1}, \vec{B}\brak{4, x, 5}, \vec{C}\brak{4,2,-2}$ and $\vec{D}\brak{6,5,-1}$ are coplanar. \hfill (12, 2017)
\item The $x$-coordinate of a point on the line joining the points $\vec{P}\brak{2, 2, 1}$and $\vec{Q}\brak{5, 1,–2}$  is $4$. Find its $z$-coordinate. \hfill (12, 2017)
\item Find the equation of plane passing through the points $\vec{A}\myvec{3 , 2 , 1}$,
      $\vec{B}\myvec{4, 2, -2}$ and $\vec{C}\myvec{6, 5, -1}$ and hence find the value of $\lambda$ for which
      $\vec{A}\myvec{3, 2 , 1}$, $\vec{B}\myvec{4 , 2 , -2}$, $\vec{C}\myvec{6 , 5 , -1}$ and $\vec{D}\myvec{\lambda , 5 , 5}$
      are coplanar. \hfill (12, 2016)
\item Show that the four points $\vec{A}(4,5,1)$, $ \vec{B}(0,-1,-1)$,
      $\vec{C}(3,9,4)$ and $\vec{D}(-4,4,4)$ are coplanar. \hfill (12, 2016)
    \item Find the equation of the line joining $\vec{A}(1, 3)$ and $\vec{B}(0, 0)$.  Also, find $k$ if $\vec{D}(k, 0)$ is a point such that the area of $\triangle{ABD}$ is $3$ square units.
\hfill (12, 2021)
    \item If
\begin{align*}
\myvec{2a+b & a-2b \\ 5c-d & 4c+3d} = \myvec{4 & -3 \\ 11 & 24},
\end{align*}
then the value of $a + b - c + 2d$ is
\hfill (12, 2021)
\item Show that the vectors $\hat{i} - 2\hat{j} + 3\hat{k}$, $2\hat{i} + 3\hat{j} - 4\hat{k}$, and $\hat{i} - 3\hat{j} + 5\hat{k}$ are coplanar. 

	\hfill (12, 2018)
\item Find the value of $x$ such that the four points with position vectors $\vec{A}(3\hat{i} + 2\hat{j} + \hat{k})$, $\vec{B}(4\hat{i} + x\hat{j} + 5\hat{k})$, $\vec{C}(4\hat{i} + 2\hat{j} - 2\hat{k})$, and $\vec{D}(6\hat{i} + 5\hat{j} - \hat{k})$ are coplanar. \hfill (12, 2018)
\item Find the value of $x$, for which the four points $\vec{A}\brak{x,1,-1}$, $\vec{B}\brak{4,5,1}$, $\vec{C}\brak{3,9,4}$ and $\vec{D}\brak{-4,4,4}$ are coplanar.
\hfill (12, 2018)
\item  Find the value of $x$ such that the four points $\vec{A}$ $\brak{x,5,-1}$,$\vec{B}$ $\brak{3,2,1}$,$\vec{C}$ $\brak{4,5,5}$ and $\vec{D}$ $\brak{4,2,-2}$ are coplanar.

\hfill (12, 2018) 
    \item The area of the triangle formed by the line $ \frac{x}{a} + \frac{y}{b} = 1 $ with the coordinate axes is 

    \hfill (10, 2023)
\end{enumerate}
