\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item Find the coordinates of the point where the line $\frac{x-1}{3} = \frac{y+4}{7} = \frac{z+4}{2}$ cuts the $xy-plane$.
\hfill (12, 2020)
    \item Find the coordinates of the point where the line through $(3, 4, 1)$ crosses the ZX-plane.
    \hfill (12, 2023)
	\item Find the equation of the line passing through $(2, -1, 2)$ and $(5, 3, 4)$ and the equation of the plane passing through $(2, 0, 3)$, $(1, 1, 5)$, and $(3, 2, 4)$. Also, find their point of intersection. \hfill (12, 2019)
	
	\item Find the vector equation of the plane which contains the line of intersection of the planes $\overrightarrow{r} \cdot (\hat{i} + 2\hat{j} + 3\hat{k}) - 4 = 0$ and $\overrightarrow{r} \cdot (2\hat{i} + \hat{j} - \hat{k}) + 5 = 0$, and which is perpendicular to the plane $\overrightarrow{r} \cdot (5\hat{i} + 3\hat{j} - 6\hat{k}) + 8 = 0$. \hfill (12, 2019)
	\item Find the vector and Cartesian equations of the plane passing through the points $(2, 5, -3)$, $(-2, -3, 5)$, and $(5, 3, -3)$. Also, find the point of intersection of this plane with the line passing through points $(3, 1, 5)$ and $(-1, -3, -1)$. \hfill (12, 2019)
	\item Find the equation of the plane passing through the intersection of the planes $\overrightarrow{r} \cdot (\hat{i} + \hat{j} + \hat{k}) = 1$ and $\overrightarrow{r} \cdot (2\hat{i} + 3\hat{j} - \hat{k}) + 4 = 0$ and parallel to the $x$-axis. Hence, find the distance of the plane from the $x$-axis. \hfill (12, 2019)
	\item Find the equation of the planes passing through the intersection of the planes $\overrightarrow{r} \cdot (3\hat{i} + 6\hat{j}) + 12 = 0$ and $\overrightarrow{r} \cdot (3\hat{i} - \hat{j} + 4\hat{k}) = 0$ and are at a unit distance from the origin. \hfill (12, 2019)
	\item Find the coordinates of the point where the line $\dfrac{x+2}{1} = \dfrac{y-5}{3} = \dfrac{z+1}{5}$ cuts the $yz$-plane. \hfill (12, 2019)
	\item Find the area of the triangle $\triangle ABC$ bounded by the lines
	\begin{align*}
	4x - y + 5 &= 0, \\
	x + y - 5 &= 0, \\
	x - 4y + 5 &= 0.
	\end{align*} \hfill (12, 2019)
\item Point $A$ lies on the line segment $XY$ joining $X(6, -6)$ and $Y(-4, -1)$ in such a way that $\frac{XA}{XY} = \frac{2}{5}$. If point $A$ also lies on the line $3x + k(y + 1) = 0$, find the value of $k$. \hfill (10, 2019)
\item Find the ratio in which the line $x - 3y = 0$ divides the line segment joining the points $(-2, -5)$ and $(6, 3)$. Find the coordinates of the point of intersection. \hfill (10, 2019)
\item Find the distance of the point $(-1, -5, -10)$ from the point of intersection of the line 
\begin{align*}
\overrightarrow{\mathbf{r}} &= \langle 2\hat{i} - \hat{j} + 2\hat{k} \rangle + \lambda \langle 3\hat{i} + 4\hat{j} + 2\hat{k} \rangle
\end{align*}
and the plane 
\begin{align*}
\overrightarrow{\mathbf{r}} \cdot \langle \hat{i} - \hat{j} + \hat{k} \rangle &= 5.
\end{align*}
\hfill (12, 2018)
\item Find the vector and Cartesian equations of the plane passing through the points $(2, 5, -3)$, $(-2, -3, 5)$, and $(5, 3, -3)$. Also, find the point of intersection of this plane with the line passing through points $(3, 1, 5)$ and $(-1, -3, -1)$. \hfill (12, 2018)
\item Find the equation of the plane passing through the intersection of the planes 
\begin{align*}
\overrightarrow{\mathbf{r}} \cdot \langle \hat{i} + \hat{j} + \hat{k} \rangle &= 1
\end{align*}
and 
\begin{align*}
\overrightarrow{\mathbf{r}} \cdot \langle 2\hat{i} + 3\hat{j} - \hat{k} \rangle + 4 &= 0
\end{align*}
and parallel to the $x$-axis. Hence, find the distance of the plane from the $x$-axis. \hfill (12, 2018)
\item Find the value of $\lambda$ for which the following lines are perpendicular to each other:
\begin{align*}
\frac{x - 5}{5\lambda + 2} &= \frac{2 - y}{5} = \frac{1 - z}{-1}
\end{align*}
\begin{align*}
\frac{x}{1} &= \frac{y + \frac{1}{2}}{2\lambda} = \frac{z - 1}{3}
\end{align*}
Hence, find whether the lines intersect or not. \hfill (12, 2018)
\item Find the equation of the plane passing through the intersection of the planes $\overrightarrow{r} \cdot\brak{\hat{i} + \hat{j} + \hat{k}}=1$ and $\overrightarrow{r} \cdot \brak{ 2\hat{i}+3\hat{j}-\hat{k}} +4=0$ and parallel to $x-axis$. Hence, find the distance of plane from $x-axis$.
\hfill (12, 2018)
\item Find the vector equation of the plane which contains the line of intersection of the planes $ \overrightarrow{r}.\brak{\hat{i} + 2\hat{j}+3\hat{k}}-4=0$ , $\overrightarrow{r}.\brak{2\hat{i} + \hat{j} - \hat{k}}+5=0$ and which is perpendicular to the plane $\overrightarrow{r}.\brak{5\hat{i} + 3\hat{j} - 6\hat{k}}+8=0$.
\hfill (12, 2018)
\item Find the equation of planes passing through the intersection  of the planes $\overrightarrow{r} \cdot \brak{2\hat{i}+6\hat{j}}+12=0$ and $\overrightarrow{r} \cdot \brak{3\hat{i}-\hat{j}+4\hat{k}}=0$ and are at a unit distance from origin.
\hfill (12, 2018) 
\item Find the value of $\lambda$, so that the lines $\frac{1-x}{3}=\frac{7y-14}{\lambda}=\frac{z-3}{2}$ and $\frac{7-7x}{3\lambda}=\frac{y-5}{1}=\frac{6-z}{5}$ are at right angles. Also, find whether the lines are intersecting or not.       
\hfill (12, 2018) 
\item Find the equation of the plane which contains the line of intersection of the planes
      \begin{align*}
          \overrightarrow{r}.\myvec{\hat{i} - 2\hat{j} + 3\hat{k}} - 4 & = 0 \text{  and} \\
          \overrightarrow{r}.\myvec{-2\hat{i} + \hat{j} + \hat{k}} + 5 & = 0
      \end{align*}
      and whose intercept on $x$-axis is equal to that of on $y$-axis. \hfill (12, 2016)
\item Find the coordinates of the point where the line through the points $P\brak{4, 3, 2}$ and $Q\brak{5,1,6}$ crosses the $XZ$ plane. Also find the angle which this line makes with the $XZ$ plane. \hfill (12, 2016)
\item Find the coordinates of the point where the line through the points $A\brak{3,4,1}$ and $B\brak{5,1,6}$ crosses the $XZ$ plane. Also find the angle which this line makes with the $XZ$ plane. \hfill (12, 2016)
\item Find the vector and cartesian equations of the plane passing through the line of intersection of planes 
$\vec{r}\cdot\brak{2\vec{i}+2\vec{j}-3\vec{k}}=7$, \quad $\vec{r}\cdot\brak{2\vec{i}+5\vec{j}+3\vec{k}}=9$
such that the intercepts made by the plane on x-axis and z-axis are equal. \hfill (12, 2015)
\item Find the equations of the diagonals of the parallelogram $PQRS$ whose vertices are $P$(4,2,-6), $Q$(5,-3,1), $R$(12,4,5) and $S$(11,9,-2). Use these equations to find the point of intersection of diagonals. \hfill (12, 2023)
\item Find the co-ordinates of the point where the line $\dfrac{x-3}{-1}=\dfrac{y+4}{1}=\dfrac{z+5}{6}$ crosses the plane passing through the points $\left(\dfrac{7}{2},0,0\right),(0,7,0),(0,0,7)$. \hfill (12, 2022)

\item Find the equation of the plane through the line of intersection of the planes
	\begin{align}
		\vec{r}\cdot(\hat{i}+3\hat{j})+6&=0\\
		\vec{r}\cdot(3\hat{i}-\hat{j}-4\hat{k})&=0
	\end{align}
	which is at a unit distance from the origin. \hfill (12, 2022)
\item Find the distance of the point $(1,-2, 9)$ from the point of intersection of the line
	\begin{align}
		\vec{r}=4\hat{i}+2\hat{j}+7\hat{k}+\lambda(3\hat{i}+4\hat{j}+2\hat{k})
	\end{align}
	and the plane
	\begin{align}
		\vec{r}\cdot(\hat{i}-\hat{j}+\hat{k})=10.
	\end{align}
\hfill (12, 2022)

\item Find the area bounded by the curves $y=\abs{x-1}$ and $y=1$, using integration. \hfill (12, 2022)

\item Find the coordinates of the point where the line through $(4,-3,-4)$ and $(3,-2,2)$ crosses the plane $2x+y+z=6$. \hfill (12, 2022)
\item Find the equation of the plane through the line of intersection of the planes 
\begin{align}
  \vec{r} \cdot \brak{i+3j} + 6 &= 0 \\  
  \vec{r} \cdot \brak{3i - j - 4k} &= 0
\end{align}
which is at a unit distance from the origin. \hfill (12, 2021)
\item Solve the system of linear equations, using matrix method : 
\begin{align}
  7x + 2y &= 11\\
  4x - y &= 2
\end{align}
\hfill (12, 2021)
\item Using the method of integration, find the area of the region bounded by the lines $3x - 2y + 1 = 0, 2x + 3y - 21 = 0$ and $x - 5y + 9 = 0$. \hfill (12, 2019)
\item Draw the graph of the equations $x - y + 1 = 0$ and $3x + 2y - 12 = 0$. Using this graph, find the values of $x$ and $y$ which satisfy both the equations.
\hfill (10, 2021)

\item Using integration, find the area of the region bounded by the line $y = 3x + 2,$ the x-axis and the ordinates $x = - 2$ and $x = 1$. \hfill (12, 2019)
\item Find the equation of the line passing through $\brak{2,-1, 2}$ and $\brak{5, 3, 4}$ and of the plane passing through $\brak{2, 0, 3}$, $\brak{1, 1, 5}$ and $\brak{3, 2, 4}$. Also, find their point of intersection. \hfill (12, 2018)
\item Find the length of the intercept, cut off by the plane $2x+y-z=5$ on the x-axis. \hfill (12, 2018)
\item Using the method of integration, find the area of the region bounded by the lines $3x-2y+1$=$0$, $2x+3y-21$ = $0$ , and  $x-5y+9$ = $0$. \hfill (12, 2018)
\item Using integration, find the area of the region bounded by the line $y = 3x + 2$, the x-axis and the ordinates and the ordinates $x=-2$ and $x=1$. \hfill (12, 2018)
\item Find the coordinates of the point where the line through the points $\brak{3, – 4, – 5}$ and $\brak{2, – 3, 1}$, crosses the plane determined by the points $\brak{1, 2, 3}, \brak{4, 2, – 3}$ and $\brak{0, 4, 3}$. \hfill (12, 2017)

\end{enumerate}
