\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item The distance between parallel planes $2x + y - 2z - 6 = 0$ and $4x + 2y - 4z = 0$ is $\rule{3cm}{0.15mm}$ units.
\hfill (12, 2020)
	\item Find the equation of the line passing through $(2, 1, -1)$ and parallel to the line $\overrightarrow{r} = (\hat{i} + \hat{j}) + \lambda (2\hat{i} - \hat{j} + \hat{k})$. Also, find the distance between these two lines. \hfill (12, 2019)
\item Find the equation of the line which passes through the point $(-2, 4, -5)$ and is parallel to the line 
	$
\frac{x + 3}{3} = \frac{4 - y}{5} = \frac{z + 8}{6}.
$
\hfill (12, 2018)
\item Find the equation of a line passing through the point $(2,3,2)$ and parallel to the line $\overrightarrow{r} = \brak{-2\hat{i}+3\hat{j}}+\lambda\brak{2\hat{i}-3\hat{j}+6\hat{k}}$. Also, find the distance between these two lines.

\hfill (12, 2018) 
\item  Find the equation of the line passing through $\brak{2, 1, -1}$ and parallel to the line $\overrightarrow{r}=\brak{\hat{i}+\hat{j}}+\lambda\brak{2\hat{i}-\hat{j}+\hat{k}}$. Also, find the distance between these two lines.

\hfill (12, 2018) 
\item Find the equation of the plane passing through the points having position vectors $\hat{i} + \hat{ j} - 2\hat{k}$, $2\hat{i}-\hat{j} + \hat{k}$ and $\hat{i} + 2\hat{j} + \hat{k}$. Write the equation of the plane passing through a point $\brak{2,3,7}$ and parllel to the plane obtained above. Hence, find the distance between the two parallel planes.
\hfill (12, 2018) 
\item Find the equation of the line which passes through the point $\brak{3,4,5}$ and is parallel to the vector $2\hat{i}+2\hat{j}-3\hat{k}$.
\hfill (12, 2018) 
\item Find the equation of the plane passing through the points $\brak{2,2,-1},\brak{3,4,2}$ and $\brak{7,0,6}$. Also find the equation of the plane passing through $\brak{4,3,1}$ and parallel to the plane obtained above.
\hfill (12, 2018) 
\item Find the equation of the plane containing two parallel lines
      $\frac{x-1}{2} = \frac{y+1}{-1} = \frac{z}{3}$ and $\frac{x}{4} = \frac{y-2}{-2} = \frac{z+1}{6}$.
      Also, find if the plane thus obtained contains the line
      $\frac{x-2}{3} =\frac{y-1}{1} = \frac{z-2}{5}$ or not. \hfill (12, 2016)

\end{enumerate}
