\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item Find the equation of the plane passing through the points $\brak{1, 0, -2}$,  $\brak{3, -1, 0}$ and perpendicular to the plane $2x - y + z = 8$. Also find the distance of the plane thus obtained from the origin.
\hfill (12, 2020)
    \item Find the values of $\lambda$ for which the distance of the point $(2, 1, \lambda)$ from the plane
$        3x + 5y + 4z = 11$
    is $2\sqrt{2}$ units.
    \hfill (12, 2023)
	\item Find the distance of the point $(a, b, c)$ from the $X$ axis. \hfill (12, 2021)
	\item If the lines $\frac{x-1}{-3} = \frac{y-2}{2\lambda} = \frac{z-3}{2}$ and $\frac{x-1}{3\lambda} = \frac{y-1}{2} = \frac{z-6}{-5}$ are perpendicular, find the value of $\lambda$. Hence, determine whether the lines intersect or not.

		\hfill (12, 2019)
	\item Find the vector equation of the plane determined by the points $\vec{A}(3, -1, 2)$, $\vec{B}(5, 2, 4)$, and $\vec{C}(-1, -1, 6)$. Hence, find the distance of the plane, thus obtained, from the origin.

		\hfill (12, 2019)
	\item Find the coordinates of the foot of the perpendicular $\vec{Q}$ drawn from $\vec{P}(3, 2, 1)$ to the plane $2x - y + z + 1 = 0$. Also, find the distance $PQ$ and the image of the point $\vec{P}$ treating this plane as a mirror. \hfill (12, 2019)
	\item Find the value of $\lambda$ for which the lines $\frac{x-5}{5(\lambda+2)} = \frac{2-y}{5} = \frac{1-z}{-1}; \frac{x}{1} = \frac{y + \frac{1}{2}}{2\lambda} = \frac{z-1}{3}.$ are perpendicular to each other.
	Hence, find whether the lines intersect or not.

		\hfill (12, 2019)
	\item Find the equation of the plane passing through the point $(-1, 3, 2)$ and perpendicular to the planes $x + 2y + 3z = 5$ and $3x + 3y + z = 0$. \hfill (12, 2019)
	
	\item Find the coordinates of the foot $\vec{Q}$ of the perpendicular drawn from the point $\vec{P}(1, 3, 4)$ to the plane $2x - y + z + 3 = 0$. Find the distance $PQ$ and the image of $\vec{P}$ treating the plane as a mirror. \hfill (12, 2019)
\item Find the coordinates of the foot of the perpendicular $\vec{Q}$ drawn from $\vec{P}(3, 2, 1)$ to the plane $2x - y + z + 1 = 0$. Also, find distance $PQ$ and the image of the point $\vec{P}$ treating this plane as a mirror.
\hfill (12, 2018)
\item Find the vector equation of the plane determined by the points $\vec{A}\brak{3,-1,2}$, $\vec{B}\brak{5,2,4}$, $\vec{C}\brak{-1,-1,6}$. Hence, find the distance of the plane, thus obtained, from the origin.

\hfill (12, 2018)
\item Find the vector equation of the plane that contains the line $\vec{r}=\brak{\hat{i}+\hat{j}}+\lambda \brak{\hat{i}+2\hat{j} - \hat{j}}$ and the point $\brak{-1,3,-4}$. Also,find the length of the perpendicular drawn from the point $\brak{2,1,4}$ to the plane, thus obtained.
\hfill (12, 2018) 
\item Find the distance between the planes
      $    \overrightarrow{r}.\myvec{2\hat{i}-3\hat{j}+6\hat{k} } - 4 =0$
      and
        $  \overrightarrow{r}.\myvec{6\hat{i}-9\hat{j} +18\hat{k}} +30 =0$
      \hfill (12, 2016)
\item Find the position vector of the foot of perpendicular and the perpendicular distance from the point $\vec{P}$ with position vector $2\hat{i}+3\hat{j}+\hat{k}$ to the plane
 $         \vec{r}\cdot\brak{2\hat{i}+\hat{j}+3\hat{k}} - 26=0$.
      Also find image of $\vec{P}$ in the plane. \hfill (12, 2016)
\item A line $l$ passes through point $(-1,3,-2)$ and is perpendicular to both the lines $\frac {x}{1}=\frac{y}{2}=\frac{z}{3}$ and $\frac {x+2}{-3}=\frac{y-1}{2}=\frac{z+1}{5}$. Find the vector equation of the line $l$. Hence, obtain its distance from origin. \hfill (12, 2023)
\item Find the equation of the plane passing through the points $(2,1,0),(3,-2,-2)$ and $(1,1,7)$. Also, obtain its distance from the origin. \hfill (12, 2022)

\item The foot of a perpendicular drawn from the point $(-2,-1,-3)$ on a plane is $(1,-3,3)$. Find the equation of the plane. \hfill (12, 2022)
\item The distance between the planes $4x-4y+2z+5=0$ and $2x-2y+z+6=0$ is
\hfill (12, 2022)
\item If the distance of the point $(1,1,1)$ from the plane $x-y+z+\lambda=0$ is $\frac{5}{\sqrt{3}}$, find the value(s) of $\lambda$. \hfill (12, 2022)

\item Find the distance of the point $(2,3,4)$ measured along the line $\frac{x-4}{3}=\frac{y+5}{6}=\frac{z+1}{2}$ from the plane $3x+2y+2z+5=0$. \hfill (12, 2022)

\item Find the distance of the point $\vec{P}(4,3,2)$ from the plane determined by the points $\vec{A}(-1,6,-5),\vec{B}(-5,-2,3)$ and $\vec{C}(2,4,-5)$. \hfill (12, 2022)

\item The distance of the line
	$	\vec{r}=(\hat{i}-\hat{j})+\lambda(\hat{i}+5\hat{j}+\hat{k})$
	from the plane
		$\vec{r}\cdot(\hat{i}-\hat{j}+4\hat{k})=5$
	is
\hfill (12, 2022)

\item Find the values of $\lambda$, for which the distance of point $(2,1,\lambda)$ from plane $3x+5y+4z=11$ is $2\sqrt{2}$ units. \hfill (12, 2022)
\item If the distance of the point $(1,1,1)$ from the plane $x-y+z+\lambda=0$ is $\frac{5}{\sqrt{3}}$, find the value(s) of $\lambda$. \hfill (12, 2022)
\item If the lines $\frac{x-1}{-3} = \frac{y-2}{2\lambda} = \frac{z-3}{2} $ and $\frac{x-1}{3\lambda} = \frac{y-1}{2}  = \frac{z-6}{-5} $ are perpendicular, find the value of $\lambda$. Hence find whether the lines are intersecting or not.
	\hfill (12, 2018)
\item Find the coordinates of the foot of perpendicular drawn from the point
      $\vec{A}(-1, 8, 4)$ to the line joining the points $\vec{B}(0, -1, 3)$ and $\vec{C}(2,-3,-1)$. Hence
      find the image of the point $\vec{A}$ in the line $BC$. \hfill (12, 2016)
\item The coordinates of the foot of the perpendicular drawn from the point $\brak{2,-3,4}$ on the $Y$ axis is
\hfill (12, 2020)
\item Find the equation of the plane passing through $\brak{-1,3,2}$ and perpendicular to the planes $x+2y+3z=5$ and $3x+3y+z=0$.
\hfill (12, 2018)
\item Find the equation of the plane passing through the intersection of the planes 
$	\overrightarrow{{r}} \cdot \brak{\hat{i} + \hat{j} + \hat{k}} = 1$
and 
$	\overrightarrow{{r}} \cdot \brak{2\hat{i} + 3\hat{j} - \hat{k} } + 4 = 0$
and parallel to the $X$ axis. Hence, find the distance of the plane from the $X$ axis.
\hfill (12, 2018)
 \item Find the value of $\lambda$ for which the lines $\frac{x-5}{5\lambda+2}= \frac{2-y}{5} = \frac{1-z}{-1};\frac{x}{1}=\frac{y+\frac{1}{2}}{2\lambda}=\frac{z-1}{3} $ are perpendicular to each other.
Hence, find whether the lines intersect or not.

\hfill (12, 2018)
\item Write the equation of the line passing through $\brak{1,2,3}$ and perpendicular to the plane $\vec{r}\cdot\brak{{i}+2{j}-5{k}}+9=0$. \hfill (12, 2015)
	\item Write the equation of a plane passing through the point $(2, 3, 7)$ and parallel to the plane obtained above. Hence, find the distance between the two parallel planes.

		\hfill (12, 2019)
	\item Find the  equation of a line passing through the point $(2, 3, 2)$ and parallel to the line $\overrightarrow{r} = (-2\hat{i} + 3\hat{j}) + \lambda (2\hat{i} - 3\hat{j} + 6\hat{k})$. Also, find the distance between these two lines.

		\hfill (12, 2019)
\end{enumerate}
