\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item Construct a triangle $ABC$ in which $BC=7cm, \angle{B}=75\degree$ and $AB + AC = 13 cm$.
\label{chapters/9/11/2/1}
	\\
	\solution 
\input{chapters/9/11/2/1/line.tex}
%
\item Construct a triangle $ABC$ in which $BC=8cm, \angle{B}=45\degree$ and $AB - AC = 3.5 cm$.
\label{chapters/9/11/2/2}
\\
\solution
\input{chapters/9/11/2/2/vector.tex}
%
\item Construct a triangle $ABC$ in which $BC=6cm, \angle{B}=60\degree$ and $AC - AB = 2cm$.
\label{chapters/9/11/2/3}
\\
\solution 
\input{chapters/9/11/2/3/line.tex}
%
\item Construct a right triangle whose base is 12$cm$ and sum of its hypotenuse and other side is 18$cm$.
\label{chapters/9/11/2/5}
\\
\solution
\input{chapters/9/11/2/5/line.tex}
%
\item Construct a triangle $ABC$ in which $\angle{B}=30\degree, \angle{C}=90\degree$ and  $AB+BC+CA=11cm$.
\label{chapters/9/11/2/4}
\\
\solution 
\input{chapters/9/11/2/4/line.tex}
%
\item Draw a right triangle ${ABC}$ in which $BC=12 cm$, $AB=5 cm$ and $\angle{B}=90\degree$.
\item Draw an isosceles triangle ${ABC}$ in which $AB=AC=6cm$ and $BC =6cm$.
\item Draw a triangle ${ABC}$ in which $AB=5cm,BC=6cm$ and $\angle {ABC}=60\degree$.
\item Draw a triangle ${ABC}$ in which $AB=4cm, BC=6cm$ and $AC=9cm$.
\item Draw a triangle ${ABC}$ in which $BC=6 cm, CA=5 cm$ and $AB=4 cm$. 
\item Is it possible to construct a triangle with lengths of its sides as 4$cm$, 3$cm$ and 7$cm$? Give reason for your answer.

\item Is it possible to construct a triangle with lengths of its sides as 9$cm$, 7$cm$ and 17$cm$? Give reason for your answer.

\item Is it possible to construct a triangle with lengths of its sides as 8$cm$, 7$cm$ and 4$cm$? Give reason for your answer.

\item Two sides of a triangle are of lengths 5$cm$ and 1.5$cm$. The length of the third side of the triangle cannot be
\begin{enumerate}
\item $3.6 cm$
\item $4.1 cm$
\item $3.8 cm$
\item $3.4 cm$
\end{enumerate}
\item The construction of a triangle $ABC$, given that $BC = 6 cm, \angle B = 45\degree$ is not possible when difference of $AB$ and $AC$ is equal to
		\begin{enumerate}
			\item 6.9$cm$
			\item 5.2$cm$
			\item 5.0$cm$
			\item 4.0$cm$
		\end{enumerate}
	\item The construction of a triangle $ABC$, given that $BC = 6 cm, \angle C = 60\degree$ is possible when difference of $AB$ and $AC$ is equal to
		\begin{enumerate}
			\item 3.2$cm$
			\item 3.1$cm$
			\item 3$cm$
			\item 2.8$cm$
		\end{enumerate}
\item Construct a triangle whose sides are $3.6 cm$, $3.0 cm$ and $4.8 cm$. Bisect the smallest angle and measure each part.
\item Construct a triangle $ABC$ in which $BC = 5 cm$, $\angle B = 60\degree$ and $AC+AB = 7.5cm$.
\end{enumerate}
Construct each of the following and give justification :
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi,resume*]
\item A triangle if its perimeter is 10.4$cm$ and two angles are 45\degree and 120\degree.
\item A triangle $PQR$ given that $QR$ = 3$cm$, $\angle PQR = 45\degree$ and $QP - PR = 2 cm$.
\item A right triangle when one side is 3.5$cm$ and sum of other sides and the hypotenuse
is 5.5$cm$.
\item An equilateral triangle if its altitude is 3.2$cm$.
\end{enumerate}                               
Write true or false in each of the following. Give reasons for your answer:
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi,resume*]
\item A triangle $ABC$ can be constructed in which $AB = 5cm, \angle A =45\degree$ and $BC + AC = 5cm$.
\item A triangle $ABC$ can be constructed in which $BC = 6cm, \angle B =30\degree$ and $AC - AB=4cm$.
\item A triangle $ABC$ can be constructed in which $\angle B =105\degree,\angle C =90\degree$ and $AB + BC + AC = 10cm$.        
\item A triangle $ABC$ can be constructed in which $\angle B =60\degree, \angle C =45 \degree$ and $AB + BC + AC = 12cm$.           
\item Draw a right triangle ${ABC}$ in which $BC=12$ cm, $AB=5$ cm and $\angle{B}=90\degree$.
\item Draw a triangle ${ABC}$ in which $AB$=4 cm, $BC=6 cm\text{ and }AC=9$. 
\item Draw a triangle ${ABC}$ in which $AB$=5 cm. $BC=6 cm\text{ and }\angle {ABC}=60\degree$. 
\item Draw a parallelogram ${ABCD}$ in which $BC=5$ cm, $AB=3$ cm and $\angle{ABC}=60\degree$, divide it into triangles ${ACB}\text{ and }{ABD}$ by the diagonal $BD$. 
Construct the triangle $BD'C'$ similar to $\triangle{BDC}$ with scale factor $\frac{4}{3}$. Draw the line segment $D'A'$ parallel to $DA$ where $\vec{A}$' lies on extended side $BA$. Is $A'BC'D'$ a parallelogram? 
\item Draw a triangle ${ABC}$ in which $BC=6$ cm, $CA=5$ cm and $AB=4$ cm. 
\end{enumerate}
