In the each of the following exercises, find the coordinates of the focus, vertex, eccentricity, axis of the conic section, the equation of the directrix and the length of the latus rectum.
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item $y^2=12x$ 
\label{chapters/11/11/2/1}
\\
\solution
\input{chapters/11/11/2/1/parab.tex}
\item 
$y^2 = –8x$
\\
\solution
\input{chapters/11/11/2/3/parab.tex}
  \item $\frac{x^2}{36}+\frac{y^2}{16}=1$
\\
\solution
\input{chapters/11/11/3/1/ellipse.tex}
  \item $\frac{x^2}{16}+\frac{y^2}{9}=1$
\\
\solution
\input{chapters/11/11/3/3/ellipse.tex}
	\item $\frac{x^2}{16}-\frac{y^2}{9} = 1$. \\ 
		\solution
		\input{chapters/11/11/4/1/hyper.tex}
\begin{table}[!ht]
\centering
\caption{}
\label{tab:std-conic-params-sol}
\resizebox{\columnwidth}{!}{%
		\input{chapters/conics/tables/std.tex}
		}
\end{table}
  \item $\frac{x^2}{4}+\frac{y^2}{25}=1$
\\
\solution
\input{chapters/11/11/3/2/ellipse.tex}
	\item $5{y^2}-9{x^2}=36$.
		\\
		\solution
		\\
		%\input{chapters/11/11/4/5/hyper.tex}
	\item $\frac{y^2}{9}-\frac{x^2}{27}=1$.
		\\
		\solution
		\\
		%\input{chapters/11/11/4/2/hyper.tex}
\item $x^2$=-16y
\\
\solution
%%\input{chapters/11/11/2/4/parab.tex}
\item $x^2$=6y 
\\
\solution
%%\input{chapters/11/11/2/2/parab.tex}
\item $x^2$=-9y  
  \item $\frac{x^2}{25}+\frac{y^2}{100}=1$
  \item $\frac{x^2}{49}+\frac{y^2}{36}=1$
  \item $\frac{x^2}{100}+\frac{y^2}{400}=1$
  \item $36x^2+4y^2=144$
  \item $16x^2+y^2=16$
  \item $4x^2+9y^2=36$
\item $y^2=10x$  
See \tabref{tab:rot-conic-params-sol}.
\begin{table}[!ht]
\centering
\caption{}
\label{tab:rot-conic-params-sol}
\resizebox{\columnwidth}{!}{%
		\input{chapters/conics/tables/rot.tex}
		}
\end{table}
\end{enumerate}

Each of the Exercises, find the equation of the conic, that satisfies the given conditions.

\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi,resume*]
\item  foci \brak{\pm 4, 0}, latus rectum of length 12.
\\
\solution
		%\input{chapters/11/11/4/13/hyper.tex}
    \item eccentricity $e = \frac{4}{3}$,
    vertices 
    \begin{align}
        \vec{P_1} = \myvec{7\\0},\ \vec{P_2} = \myvec{-7\\0}
        \label{eq:chapters/11/11/4/14/vert}
    \end{align}
\\
\solution
		%\input{chapters/11/11/4/14/hyper.tex}
\item centre at (0,0), major axis on the y-axis and passes through the points (3,2) and (1,6).
\\
\solution
%%\input{chapters/11/11/3/19/ellipse.tex}
\item major axis on the x-axis and passes through the points (4,3) and (6,2).
\\
\solution
%%\input{chapters/11/11/3/20/ellipse.tex}
\item vertices $\myvec{0\\\pm 3}$ and foci $\myvec{0\\\pm5}$.
	\\
\solution
		%\input{chapters/11/11/4/9/hyper.tex}
	%\input{chapters/11/11/4/8/hyper.tex}
\item focus(6,0); directrix x=-6 
\item focus(0,-3); directrix y=3
\item vertex(0,0); focus(3,0)
\item vertex(0,0); focus(-2,0) 
\item vertex(0,0) passing through(2,3) and axis is along x-axis
\item vertex(0,0) passing through(5,2) symmetric with respect to y-axis
\item vertices $\brak{0,\pm 5}, \text{foci} \brak{0,\pm 8}$.  
\item vertices $(\pm5,0),\text{foci} (\pm4,0)$.
\item vertices $(\pm0,13),\text{foci} (0,\pm5)$.
\item vertices $(\pm6,0),\text{foci} (\pm4,0)$.
\item ends of major axis $(\pm3,0)$, ends of minor axis $(0,\pm2)$.
\item ends of major axis $(0,\pm \sqrt{5})$, ends of minor axis $(\pm1,0)$.
\item length of major axis 26, foci $(\pm5,0)$.
\item length of minor axis 16, foci $(0,\pm6)$.
\item foci $(\pm3,0),a=4$.
\item vertex (0,4),  focus (0,2). 
\item vertex (-3,0),  directrix $x+5=0$.
\item focus (0,-3) and directrix y=3.
\item  Directrix x=0. focus ot (6,0)
\item  vertex  ot (0,4), focus at (0,2)
\item  focus at (-1,2), directrix x-2y+3=0
	 \item  vertices $(\pm5,0)$, foci $(\pm 7,0)$
	 \item vertices $(0\pm7)$ ,e =$\frac{4}{3}$ 
	 \item  foci (0,$\pm\sqrt{10})$. passing through (2,3)
\item vertices at $(0,\pm6)$,  eccentricity $\frac{5}{3}$
\item focus (-1,-2),  directrix $x-2y+3=0$ 
\item eccentricity $\frac{3}{2}$, foci $(\pm2,0)$.
\item If the parabola $y^2=4ax$ passes through the point (3,2), then the length of its latus rectum is
\begin{enumerate}
\item 2$\pm$3
\item 4$\pm$4
\item 1$\pm$3
\item 4
\end{enumerate}
 \item Find the coordinates of a point on the parabola $y^2=8x$ whose focal distance is 4.
 \item Find the length of the line segment joining the vertex of the parabola $y^2=4ax$ and a point on the parabola where the line segment makes an angle 0 to the x-axis.
\end{enumerate}
Fill in the Blanks
\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi,resume*]
\item show that the set of all points such that the difference of their distances from (4,0) and (-4,0) is always equal to 2 represent a hyperbola .
\item If the distance between the foci of a hyperbola is 16 and its eccentricity is $\sqrt{2}$, then obtain the equation of the hyperbola.
\item Find the eccentricity of the hyperbola $9y^2-4x^2=36$.
\item The eccentricity of the hyperbola whose latus rectum is 8 and conjugate axis is equal to half of th distance between the foci is 
\begin{enumerate}
\item $4\pm3$
\item $\frac{4}{\sqrt{3}}$
\item $\frac{2}{\sqrt{3}}$
\item none of these
\end{enumerate}
\item The distance between the foci of a hyperbola is 16 and its eccentricity is $\le{2}$. lts equation is
\begin{enumerate}
\item $x^2-y^2=3^2$
\item $\frac{x^2}{4-}\frac{y^2}{9}=1$
\item $2x-3y^2=7$
 \item none of these
 \end{enumerate}
 \item Equation of the hyperbola with eccentricty 3$\pm$2 and foci at ($\pm2,0)$ is
\begin{enumerate} 
	\item $\frac{x^2}{4}-\frac{y^2}{5}=\frac{4}{9}$

	\item  $\frac{x^2}{9}-\frac{y^2}{9}=\frac{4}{9}$
	\item  $\frac{x^2}{4}-\frac{y^2}{9}=1$
\item  none of these.
\end{enumerate}
 \item If the latus rectum of an ellipse is equal to half of minor axis, then find its eccentricity.
 \item Given the ellipse with equation $9x^2+25y^2=225,$ find the eccentricity and focl.
 \item If the eccentricity of an ellipse is $\frac{5}{8}$ and  the distance between its foci is 10 then find latus rectum of the ellipse.
 \item eccentricity $\frac{2}{3}$, latus rectum 5, centre  (0,0).
 \item Find the distance between the directrices of the ellipse $\frac{x^2}{36}+\frac{y^2}{20}$
\item Find the equation of the set of all points the sum of whose distances  from the points (3,0) and (9,0) is 12.
\item Find the equation of the set of all points whose distance from (0,4) are 2$\pm$3 of their distance from the line y=9.
\item The equation of the ellipse whose focus is (1,-1), the directrix the line $x-y-3
=0$ and eccentricity $1 \pm 2$ is
\begin{enumerate}
\item $7x^2+2xy+7y^2-10x+10y+7=0$
\item $7x^2+2xy+7y^2+7=0$
\item $7x^2+2xy+7y^2+10x-10y-7=0$ 
\item none
\end{enumerate}
\item The length of the latus rectum of the ellipes $3x^2+y^2=12$ is
\begin{enumerate}
\item 4
\item 3
\item 8
\item $4\sqrt{3}$
\end{enumerate}
\item If ${P}$ is a point on the ellipse $\frac{x^2}{16}+\frac{y^2}{25}=1$ whose foci  are $s$ and $s'$ then $Ps +Ps'=8$.
\end{enumerate}
