\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item  The cable of a uniformly loaded suspension bridge hangs in the form of a parabola. The roadway which is horizontal and 100 m long is supported by vertical wires attached to the cable, the longest wire being 30 m and the shortest being 6 m. Find the length of a supporting wire attached to the roadway 18 m from the middle.
\label{chapters/11/11/5/3}
\\
\solution
\input{chapters/11/11/5/3/parab.tex}
    \item Find the area of the triangle formed by the lines joining the vertex 
    of the parabola 
    \begin{align}
        x^2 = 12y
        \label{eq:chapters/11/11/5/6/parabola}
    \end{align}
    to the ends of its latus rectum.
\label{chapters/11/11/5/6}
\\
\solution
\input{chapters/11/11/5/6/parab.tex}
\item A man running a racecourse notes that the sum of the distances from the two flag posts from him is always 10 m and the distance between the flag posts is 8 m. Find the equation of the posts traced by the man. 
\label{chapters/11/11/5/7}
 \item Find the coordinates of a point on the parabola $y^2=8x$ whose focal distance is 4.
\item Show that the set of all points such that the difference of their distances from (4,0) and (-4,0) is always equal to 2 represent a hyperbola.
\item If the distance between the foci of a hyperbola is 16 and its eccentricity is $\sqrt{2}$, then obtain the equation of the hyperbola.
\item The eccentricity of the hyperbola whose latus rectum is 8 and conjugate axis is equal to half of the distance between the foci is 
\begin{enumerate}
\item $\frac{4}{3}$
\item $\frac{4}{\sqrt{3}}$
\item $\frac{2}{\sqrt{3}}$
\item none of these
\end{enumerate}
\item The distance between the foci of a hyperbola is 16 and its eccentricity is $\le{2}$. lts equation is
\begin{enumerate}
\item $x^2-y^2=3^2$
\item $\frac{x^2}{4-}\frac{y^2}{9}=1$
\item $2x-3y^2=7$
 \item none of these
 \end{enumerate}
 \item If the latus rectum of an ellipse is equal to half of minor axis, then find its eccentricity.
 \item If the eccentricity of an ellipse is $\frac{5}{8}$ and  the distance between its foci is 10 then find latus rectum of the ellipse.
 \item Find the distance between the directrices of the ellipse $\frac{x^2}{36}+\frac{y^2}{20}$
\item Find the equation of the set of all points the sum of whose distances  from the points (3,0) and (9,0) is 12.
\item If ${P}$ is a point on the ellipse $\frac{x^2}{16}+\frac{y^2}{25}=1$ whose foci  are $s$ and $s'$ then $Ps +Ps'=8$.
\item An arch is in the form of a parabola with its axis vertical. The arch is 10m high and 5m wide at the base. How wide is it 2m from the vertex of the parabola?
\label{chapters/11/11/5/2}
\item An equilateral triangle is inscribed in the parabola $y^{2} = 4ax$,where one vertex is at the vertex of the parabola. Find the length of the side of the triangle.
\label{chapters/11/11/5/8}
\item An arch is in the form of a semi-ellipse. It is 8 m wide and 2 m high at the centre. Find the height of the arch at a point 1.5 m from one end.
\label{chapters/11/11/5/4}
\item A rod of length 12cm moves with its ends always touching the coordinate axes. Determine the equation of locus of a point  P on the rod, which is 3cm from the end in contact with $x-axis$.
\label{chapters/11/11/5/5}
\end{enumerate}
Find the roots of the following quadratic  equations grapically.
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi,resume*]
\item $x^2-3x-10=0$
\item $2x^2+x-6=0$
\item $ \sqrt 2x^2+7x+5 \sqrt 2=0$
\item $2x^2-x+\frac{1}{8}=0$
\item $100x^2-20x+1=0$
\item $2x^2-3x+5=0$
\item $3x^2-4 \sqrt 3x+4=0$
\item $2x^2-6x+3=0$
\item $(x+1)^2=2(x-3)$
\item $x^2-2x=(-2)(3-x)$
\item $(x-3)(2x-1)=x(x+5)$
\item $(2x-1)(x-3)=(x+5)(x-1)$
\end{enumerate}
Find the values of k for each of the following quadratic equations, so that they have equal roots.  Verify your solution graphically.
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi,resume*]
\item $2x^2=kx-3=0$.
\item $kx(x-2)+6=0$.
\end{enumerate}
Represent the following situations graphically.
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi,resume*]
\item John and Jivanti together have $45$ marbles. Both of them lost $5$ marbles each, and the product of the number of marbles they have is $124$. We would like to find out how many marbles they had to start with.
\item A cottage industry produces a certain number of toys in a day. The cost of production of each toy (in rupees) was found to be $55$ minus the number of toys produced in a day. On a particular day, the total cost of production was \rupee~750. We would like to find out the number of toys produced on that day.
\item Find two numbers whose sum is $27$ and product is $182$.
\item Find two consecutive  positive integers, sum of whose squares is $365$.
\item  The altitude of a right triangle is 7 cm less than its base. If the hypotenuse is 13 cm, find the other two sides.
\item A cottage industry produces a certain number of pottery articles in a day. It was observed on a particular day that the cost of production of each article (in rupees) was $3$ more than twice the number of articles produced on that day. If the total cost of production on that day was \rupee~90, find the number of articles produced and the cost of each article.
\item Is it possible to design a rectangular mango grove whose length is twice its breadth, and the area is  $800m^2$? If so, find its length and breadth.
\item Is the following situation possible? If so, determine their present ages.
\\ The sum of the ages of the two friends is 20 years. Four years ago, the product of their ages in years was $48$.
\item Is it possible to design a rectangular park of perimeter 80m and area of $400m^2$. If so, find its length and breadth.
\item The area of rectangulr plot is $528m^2$. The length of the plot (in metres) is one more than twice its breadth. We need to find the length and breadth of the plot.
\item The product of two consecutive positive integers is $306$. We need to find the integers.
\item Rohan's mother is $26$ years older than him. The product of their ages(in years) $3$ years from now will be $360$. We would like to find Rohan's present age.
\item A train travels a distance of $480km$ at a unifom speed. If the speed had been $8km/h$ less, then it would have taken $3 hours$ more to cover the same distance. We need to find the speed of the train.
\end{enumerate}
