\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item The distance between the points \brak{m, -n} and \brak{-m, n} is
\begin{enumerate}
\item \(\sqrt{m^{2} + n^{2}}\)
\item \(m + n\)
\item \(2\sqrt{m^{2} + n^{2}}\)
\item \(\sqrt{2m^{2} + 2n^{2}}\)
\end{enumerate}
\hfill (10, 2020)

\item The point on the $X$ axis which is equidistant from \brak{-4,0} and \brak{10,0} is
\begin{enumerate}
\item \brak{7,0}
\item \brak{5,0}
\item \brak{0,0}
\item \brak{3,0}
\end{enumerate}
\hfill (10, 2020)
%
\item \(AOBC\) is a rectangle whose three vertices are \brak{0, -3}, \brak{0, 0} and \brak{4, 0}. The length of its diagonal is
\hfill (10, 2020)
\item If $\mydet{\overrightarrow{a}}= 4$ and $-3 \leq \lambda \leq 2$, then $\mydet{\lambda \overrightarrow a}$ lies in
\begin{enumerate}
\item $\sbrak{0,12}$
\item $\sbrak{2,3}$
\item $\sbrak{8,12}$
\item $\sbrak{-12,8}$
\end{enumerate}
\hfill (12, 2020)
    \item The distance between the point $(0,2\sqrt{5})$ and $(-2\sqrt{5},0)$ is
    \hfill (10, 2023)
    \item If $\vec{Q} = (0,1)$ is equidistant from $CA = (5,-3)$ and $\vec{R} = (x,6)$, find the value of $x$.
    \hfill (10, 2023)
    \item The distance of the point $(-6,8)$ from the origin is
    \hfill (10, 2023)
    \item The distance between the points $(0,0)$ and $(a-b, a+b)$ is 
    \hfill (10, 2022)
	\item Find the distance between the points $\vec{A}\left(-\frac{7}{3}, 5\right)$ and $\vec{B}\left(\frac{2}{3}, 5\right)$. \hfill (10, 2021)
		\item The distance between the points $\vec{A}(0, 6)$ and $\vec{B}(0, -2)$ is
		\hfill (10, 2021)
		\item If the distance between the points $(k, -2)$ and $(3, -6)$ is $10$ units, find the positive value of $k$. \hfill (10, 2021)
		\item Find the length of the segment joining $\vec{A}(-6, 7)$ and $\vec{B}(-1, -5)$. Also, find the midpoint of $AB$. \hfill (10, 2021)
	
	\item A man goes $5$ meters due west and then $12$ meters due north. How far is he from the starting point? \hfill (10, 2021)
		\item If $\vec{P}(2, 2)$, $\vec{Q}(-4, -4)$, and $\vec{R}(5, -8)$ are the vertices of a triangle $\triangle PQR$, then find the length of the median through $\vec{R}$. \hfill (10, 2021)
	\item If $\vec{a}, \vec{b}, \vec{c}$ are position vectors of the points $A(2, 3, -4)$, $B(3, -4, -5)$, and $C(3, 2, -3)$ respectively, then $\abs{\vec{a}+\vec{b}+\vec{c}}$ is equal to
		\begin{enumerate}
			\item $\sqrt{113}$
			\item $\sqrt{185}$
			\item $\sqrt{203}$
			\item $\sqrt{209}$
		\end{enumerate}
	\hfill (12, 2021)
\item Find the distance between the points $(a, b)$ and $(-a, -b)$. \hfill (10, 2019)
\item Write the coordinates of a point $P$ on the $x$-axis which is equidistant from the points $A(-2, 0)$ and $B(6, 0)$. \hfill (10, 2019)
\item Find the value of $x$ if the distance between the points $A(0, 0)$ and $B(x, -4)$ is 5 units. \hfill (10, 2019)
\item Find the values of $x$ for which the distance between the points $A(x, 2)$ and $B(9, 8)$ is 10 units. \hfill (10, 2019)
\item Find the point on the $y$-axis which is equidistant from the points $(5, -2)$ and $(-3, 2)$. \hfill (10, 2019)
    \item Given vertices of a parallelogram $\vec{A}(-2,1)$, $\vec{B}(a,0)$, $\vec{C}(4,b)$, and $\vec{D}(1,2)$. Find the values of $a$ and $b$. Hence, find the lengths of its sides. \hfill (10, 2018)
    \item Find the value of $y$ for which the distance between the points $\vec{P}(2,-3)$ and $\vec{Q}(10,y)$ is $10$ units. \hfill (10, 2018)
    \item If the point $\vec{P}(0,2)$ is equidistant from the points $\vec{Q}(3,k)$ and $\vec{R}(k,5)$, find the value of $k$. \hfill (10, 2018)
    \item The x-coordinate of a point $\vec{P}$ is twice its y-coordinate. If $\vec{P}$ is equidistant from the points $\vec{Q}(2,-5)$ and $\vec{R}(-3,6)$, find the coordinates of $\vec{P}$. \hfill (10, 2018)
    \item If the point $P \myvec{x, y}$ is equidistant from the points $A \myvec{a+b, b-a}$ and $B \myvec{a-b, a+b}$, prove that $bx = ay$. \hfill (10, 2016)
\item The distance of the point $\brak{-3,4}$ from the $x$-axis is
\hfill (10, 2012)
\item Find the value of $k$, if the point $P\brak{2,4}$ is equidistant from the points $A\brak{5,k}$ and $B\brak{k,7}$. 
\hfill (10, 2012)
\item If a point $A\brak{0,2}$ is equidistant from the points $B\brak{3,p}$ and $C\brak{p,5}$, then find the value of $p$. 
\hfill (10, 2012)
\item If $A$ and $B$ are the points $(-6, 7)$ and $(-1, -5)$ respectively, then the distance $2AB$ is equal to
\hfill (10, 2011)
\item Find the value of $y$ for which the distance between the points $A(3, -1)$ and $B(11, y)$ is $10$ units.
\hfill (10, 2011)
\item The distance between the points $\brak{m,-n}$ and $\brak{-m, n}$ is
\hfill (10, 2020)
\item The point on the x-axis which is equidistant from $\brak{-4,0}$ and $\brak{10,0}$ is
\hfill (10, 2020)
\item $AOBC$ is a rectangle whose three vertices are $\vec{A}\brak{0,-3}$, $\vec{O}\brak{0,0}$ and $\vec{B}\brak{4,0}$. The length of its diagonal is $\rule{3cm}{0.15mm}$.
\hfill (10, 2020)
\end{enumerate}
