\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item The centre of a circle whose end points of a diameter are \brak{-6,3} and \brak{6,4} is
\rule{1cm}{0.2pt}.

\hfill (10, 2020)
\item Find the ratio in which the $Y$ axis  divides the line segment joining the points \brak{6, -4} and \brak{-2, -7}. Also find the point of intersection.
\hfill (10, 2020)
    \item In what ratio does the $X$ axis divide the line segment joining the points $\vec{A}(3,6)$ and $\vec{B}(-12, -3)$?
    \hfill (10, 2023)
    \item A circle has its center at $(4,4)$. If one end of a diameter is $(4,0)$, then find the coordinates of the other end.
    \hfill (10, 2022)
	\item Find the coordinates of the point which divides the line segment joining the points $\vec{A}(7, -1)$ and $\vec{B}(-3, -4)$ in the ratio $2:3$. \hfill (10, 2021)
		\item The point which divides the line segment joining the points $(7, -6)$ and $(3, 4)$ in the ratio $1:2$ is
\rule{1cm}{0.2pt}.
		\hfill (10, 2021)
		\item If $\left(\frac{a}{3}, 4\right)$ is the midpoint of the line segment joining the points $(-6, 5)$ and $(-2, 3)$, then the value of $a$ is
		\hfill (10, 2021)
		\item Find the ratio in which $\vec{P}(4, 5)$ divides the line segment joining $\vec{A}(2, 3)$ and $\vec{B}(7, 8)$.

			\hfill (10, 2021)
		\item Find the ratio in which the $Y$ axis divides the line segment joining the points $\vec{A}(5, -6)$ and $\vec{B}(-1, -4)$. Also, find the coordinates of the point of intersection. \hfill (10, 2021)
		\item Find the ratio in which the line segment joining the points $\vec{A}(1, -5)$ and $\vec{B}(-4, 5)$ is divided by the $X$ axis. Also, find the coordinates of the point of division. \hfill (10, 2021)
\item The point $\vec{R}$ divides the line segment $AB$, where $\vec{A}(-4, 0)$ and $\vec{B}(0, 6)$ such that $AR = \frac{3}{4} AB$. Find the coordinates of $\vec{R}$. \hfill (10, 2019)
\item In what ratio does the point $\vec{P}(-4, y)$ divide the line segment joining the points $\vec{A}(-6, 10)$ and $\vec{B}(3, -8)$? Hence, find the value of $y$. \hfill (10, 2019)
\item Find the ratio in which the $Y$ axis divides the line segment joining the points $(-1, -4)$ and $(5, -6)$. Also find the coordinates of the point of intersection. \hfill (10, 2019)
\item Points $\vec{P}$ and $\vec{Q}$ trisect the line segment joining the points $\vec{A}(-2, 0)$ and $\vec{B}(0, 8)$ such that $\vec{P}$ is nearer to $\vec{A}$. Find the coordinates of points $\vec{P}$ and $\vec{Q}$. \hfill (10, 2019)
\item The midpoint of the line segment joining $\vec{A}(2a, 4)$ and $\vec{B}(-2, 3b)$ is $(1, 2a + 1)$. Find the values of $a$ and $b$. \hfill (10, 2019)
\item Find the coordinates of a point $\vec{A}$ where $AB$ is a diameter of the circle with center $(3, -1)$ and the point $\vec{B}$ is $(2, 6)$. \hfill (10, 2019)
\item The midpoint of the line segment joining $\vec{A}(2a, 4)$ and $\vec{B}(-2, 3b)$ is $(1, 2a + 1)$. Find the values of $a$ and $b$. \hfill (10, 2019)
\item Find the coordinates of a point $\vec{A}$ where $AB$ is the diameter of a circle whose center is $(2, -3)$ and $\vec{B}$ is the point $(1, 4)$. \hfill (10, 2019)
\item Find the ratio in which the segment joining the points $(1, 3)$ and $(4, 5)$ is divided by the $X$ axis. Also find the coordinates of this point on the $X$ axis. \hfill (10, 2019)
\item Find the coordinates of a point $\vec{A}$ where $AB$ is a diameter of the circle with center $(-2, 2)$ and $\vec{B}$ is the point $(3, 4)$. \hfill (10, 2019)
    \item Find the ratio in which $\vec{P}(4,m)$ divides the line segment joining the points $\vec{A}(2,3)$ and $\vec{B}(6,-3)$. Hence, find $m$. \hfill (10, 2018)
\item $\vec{X}$ and $\vec{Y}$ are two points with position vectors $3\overrightarrow{a}+\overrightarrow{b}$ and$\overrightarrow{a}-3\overrightarrow{b}$ respectively. Write the position vector of a point $\vec{V}$ which divides the line segment $XY$ in the ratio $2:1$ externally.
\hfill (12, 2018) 
\item Show that the points $\vec{A}\brak{-2\hat{i} + 3\hat{j} + 5\hat{k}}$, $\vec{B}\brak{\hat{i} + 2\hat{j} + 3\hat{k}}$ and $\vec{C}\brak{7\hat{i} -\hat{k} }$ are collinear.

\hfill (12, 2018) 
\item A line intersects the $Y$ axis and $X$ axis at the points $\vec{P} = (0, b)$ and $\vec{Q} = (c, 0)$ respectively. If $(2, -5)$ is the midpoint of $PQ$, then find the coordinates of $\vec{P}$ and $\vec{Q}$.

	\hfill (10, 2017)
\item In what ratio does the point $\left(\frac{24}{11}, y\right)$ divide the line segment joining the points $\vec{P} = (2, -2)$ and $\vec{Q} = (3, 7)$? Also find the value of $y$. \hfill (10, 2017)
    \item Let $\vec{P}$ and $\vec{Q}$ be the points of trisection of the line segment joining the points $\vec{A} \myvec{2,-2}$ and $\vec{B} \myvec{-7, 4}$ such that $\vec{P}$ is nearer to $\vec{A}$. Find the coordinates of $\vec{P}$ and $\vec{Q}$.
	    
	    \hfill (10, 2016)
    \item If the coordinates of points $\vec{A}$ and $\vec{B}$ are $\brak{-2, -2}$ and $\brak{2, -4}$ respectively, find the coordinates of $\vec{P}$ such that $AP = \frac{3}{7} AB$, and $\vec{P}$ lies on the line segment $AB$. 

		\hfill (10, 2015)
\item  $\vec{P}\brak{5,-3}$ and $\vec{Q}\brak{3,y}$ are the points of trisection of the line segment joining $\vec{A}\brak{7,-2}$ and $\vec{B}\brak{1,-5}$. Then $y$ equals
\hfill (10, 2012)
\item The coordinates of the point $\vec{P}$ dividing the line segment joining the points $\vec{A}\brak{1,3}$ and $\vec{B}\brak{4,6}$, in the ratio $2:1$ are
\hfill (10, 2012)
\item If the coordinates of one end of a diameter of a circle are $\brak{2,3}$ and the coordinates of its centre are $\brak{-2,5}$, then the coordinates of the other end of the diameter are
\rule{1cm}{0.2pt}.

\hfill (10, 2012)
\item Find the coordinates of a point $\vec{P}$, which lies on the line segment joining the points $\vec{A}\brak{-2,2}$ and $\vec{B}\brak{2,-4}$ such that $AP = \dfrac{3}{7} AB$. 
\hfill (10, 2012)
\item Find the ratio in which the line segment joining the points $\brak{1,-3}$ and $\brak{4,5}$ is divided by $X$ axis. 
\hfill (10, 2012)
\item Find the ratio in which the $Y$ axis divides the line segment joining the points $\brak{5,-6}$ and $\brak{-1,-4}$. Also find the coordinates of the point of intersection. 
\hfill (10, 2012)
    \item The point $\vec{P}$ which divides the line segment joining the points $\vec{A}(2, - 5)$ and $\vec{B}(5, 2)$ in the ratio 2:3 lies in which quadrant?
\hfill (10, 2011)
    \item The mid-point of segment AB is the point $\vec{P}( 0, 4)$. If the coordinates of $\vec{B}$ are (-2, 3) then the coordinates of $\vec{A}$ are
\hfill (10, 2011)
\item Point $\vec{P}(x, 4)$ lies on the line segment joining the points $\vec{A} (-5,8)$ and $\vec{B} (4, -10)$. Find the ratio in which point $\vec{P}$ divides the line segment $AB$. Also, find the value of $x$.

\hfill (10, 2011)
\item The centre of a circle whose end points of a diameter are $\brak{-6,3}$ and $\brak{6,4}$ is
\rule{1cm}{0.2pt}.

\hfill (10, 2020)
\item Find the ratio in which the $Y$ axis divides the line segment joining the points $\brak{6,-4}$ and $\brak{-2, -7}$. Also find the point of intersection.
\hfill (10, 2020)
\end{enumerate}
