\begin{enumerate}[label=\thesubsection.\arabic*,  ref=\thesubsection.\theenumi]
\item Find a vector $\overrightarrow{r}$ equally inclined to the three axes and whose magnitude is $3\sqrt{3}$ units.
\hfill (12,  2020)
    \item Unit vector along $PQ$,  where coordinates of $\vec{P}$ and $\vec{Q}$ respectively are (2, 1, -1) and (4, 4, -7),  is
    \hfill (12,  2023)
    \item If a line makes $60\degree$ and $45\degree$ angles with the positive directions of the $X$ axis and $Z$ axis respectively, then find the angle that it makes with the positive direction of the Y-axis. Hence, write the direction cosines of the line.
    \hfill (12, 2023)
    \item A vector of magnitude $9$ units in the direction of the vector $-2\hat{i} - \hat{j} + 2\hat{k}$ is \underline{\hspace{1cm}}.
	\item The scalar product of the vector $\overrightarrow{a} = \hat{i} + \hat{j} + \hat{k}$ with a unit vector along the sum of the vectors $\overrightarrow{b} = 2\hat{i} + 4\hat{j} - 5\hat{k}$ and $\overrightarrow{c} = \hat{\lambda} + 2\hat{j} + 3\hat{k}$ is equal to $1$. Find the value of $\lambda$ and hence find the unit vector along $\overrightarrow{b} + \overrightarrow{c}$. \hfill (12, 2019)
    \hfill (12, 2022)
	\item Find the direction cosines of a line which makes equal angles with the coordinate axes. \hfill (12, 2019)
	\item If a line has the direction ratios $-18, 12, -4$, then what are its direction cosines? \hfill (12, 2019)
	\item Find the direction cosines of the line joining the points $P(4, 3, -5)$ and $Q(-2, 1, -8)$. \hfill (12, 2019)
\item If a line has direction ratios $-18, 12, -4$, what are its direction cosines? \hfill (12, 2018)
\item Find a unit vector perpendicular to both the vectors $\overrightarrow{a} = \hat{i} - 7\hat{j} + 7\hat{k}$ and $\overrightarrow{b} = 3\hat{i} - 2\hat{j} + 2\hat{k}$. \hfill (12, 2018)
\item Find the equation of the plane passing through the intersection of the planes 
\begin{align*}
\overrightarrow{\mathbf{r}} \cdot \langle \hat{i} + \hat{j} + \hat{k} \rangle &= 1
\end{align*}
and 
\begin{align*}
\overrightarrow{\mathbf{r}} \cdot \langle 2\hat{i} + 3\hat{j} - \hat{k} \rangle + 4 &= 0
\end{align*}
and parallel to the $x$-axis. Hence, find the distance of the plane from the $x$-axis. \hfill (12, 2018)
\item Find the direction cosines of the line joining points $P(4, 3, -5)$ and $Q(-2, 1, 8)$. \hfill (12, 2018)
\item Find the direction cosines of the line joining points $P$ $\brak{4,3,-5}$ and $Q$ $\brak{-2,1,8}$.
\hfill (12, 2018)
 \item Find the value of $\lambda$ for which the following lines are perpendicular to each other:
 \begin{align*}
 \dfrac{x-5}{5\lambda+2}= \dfrac{2-y}{5} = \dfrac{1-z}{-1};\dfrac{x}{1}=\dfrac{y+\dfrac{1}{2}}{2\lambda}=\dfrac{z-1}{3} 
 \end{align*}
Hence, find whether the lines intersect or not.
\hfill (12, 2018)
\item The scalar product of the vector $\overrightarrow{a} = \hat{i} + \hat{j} + \hat{k}$ with a unit vector along the sum of the vector $\overrightarrow{b} = 2\hat{i} + 4\hat{j} - 5\hat{k}$ and $\overrightarrow{c} = \lambda \hat{i} + 2\hat{j} + 3\hat{k}$ is equal to $1$. Find the value of $\lambda$ and hence find the unit vector along $\overrightarrow{b} + \overrightarrow{c}$.
\hfill (12, 2018) 
\item If the sum of two unit vectors is a unit vector, prove that the magnitude of their difference is $\sqrt{3}$.
\hfill (12, 2018) 
\item If a line makes angles $ 90\degree,135\degree,45\degree$ with the x,y and z axes respectively,find its direction cosines.
\hfill (12, 2018) 
\item If the distances of $\vec{P} = (x, y)$ from $\vec{A} = (5, 1)$ and $\vec{B} = (-1, 5)$ are equal, then prove that $3x = 2y$. \hfill (10, 2017)
\item If $\overrightarrow{a} = 4\hat{i} - \hat{j} +\hat{k}$ and $\overrightarrow{b} = 2\hat{i} - 2\hat{j} + \hat{k}$, then find a unit vector parallel to the vector $\overrightarrow{a}+\overrightarrow{b}$. \hfill (12, 2016)
\item Write the direction ratios of the vector $3\vec{a}+2\vec{b}$ where $\vec{a} = \vec{i}+\vec{j}-2\vec{k}$ and $\vec{b} = 2\vec{i}-4\vec{j}+5\vec{k}$. \hfill (12, 2015)
\end{enumerate}
