\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item A fraction becomes $\frac{1}{3}$ when $1$ is subtracted from the numerator and it becomes $\frac{1}{4}$ when $8$ is added to its denominator. Find the fraction.
\hfill (10, 2020)
\item The present age of a father is three years more than three times the age of his son. Three years hence the father's age will be $10$ years more than twice the age of the son. Determine their present ages.
\hfill (10, 2020)
\item Two schools $P$ and $Q$ decided to award prizes to their students for two games of Hockey \rupee $x$ per students and cricket \rupee $y$ per student. School $P$
decided to award a total of \rupee $9,500$ for the two games to $5$ and $4$ students respectively; while school $Q$ decided to award \rupee $7,370$ for the two games to $4$ and $3$ students respectively.
Based on the given information, answer the following questions :
\begin{enumerate}
    \item Represent the following information algebraically (in terms of $x$ and $y$).
    \item\begin{enumerate}
\item What is the prize amount for hockey ?
\item Prize amount on which game is more and by how much ?
    \end{enumerate}
    \item What will be the total prize amount if there are $2$ students each from two games ?
\end{enumerate}
\hfill (10, 2020)
\item Half of the difference between two numbers is $2$. The sum of the greater number and twice the smaller number is $3$. Find the numbers.
\hfill (10, 2023)
    \item The sum of the numerator and the denominator of a fraction is $18$. If the denominator is increased by $2$, the fraction reduces to $\frac{1}{3}$. Find the fraction.
\hfill (10, 2021)
    \item If $2$ tables and $2$ chairs cost \rupee $700$ and $4$ tables and $3$ chairs cost \rupee $1,250$, then find the cost of one table.
\hfill (10, 2021)
\item A part of monthly hostel charges in a college hostel are fixed and the remaining depends on the number of days one has taken food in the mess. When a student $A$ takes food for $25$ days, he has to pay {\rupee $4,500$}, whereas a student $B$ who takes food for $30$ days, has to pay {\rupee $5,200$}. Find the fixed charges per month and the cost of food per day.
\hfill (10, 2019)


\item A father's age is three times the sum of the ages of his two children. After $5$ years his age will be two times the sum of their ages. Find the present age of the father.
\item A boat goes $30 \,\text{km}$ upstream and $44 \,\text{km}$ downstream in $10$ hours. In $13$ hours, it can go $40\,\text{km}$ upstream and $55 \,\text{km}$ downstream. Determine the speed of the stream and that of the boat in still water.
\hfill (10, 2019)

\item A fraction becomes $\frac{1}{3}$ when $2$ is subtracted from the numerator and it becomes $\frac{1}{2}$ when $1$ is subtracted from the denominator. Find the fraction.
\hfill (10, 2019)

\item Sumit is $3$ times as old as his son. Five years later, he shall be two and a half times as old as his son. How old is Sumit at present ?
\hfill (10, 2019)
    \item Ishan wants to donate a rectangular plot of land for a school in his village. When he was asked to give dimensions of the plot, he told that if its length is decreased by $50m$ and breadth is increased by $50m$, then its area will remain same, but if length is decreased by $10m$ and breadth is decreased by $20m$, then its area will decrease by $5300m^2$. Using matrices, find the dimensions of the plot. Also give reason why he wants to donate the plot for a school.
\hfill (10, 2016)
    \item A shopkeeper has $3$ varieties of pens $A$, $B$ and $C$. Meenu purchased $1$ pen of each variety for a total of \rupee $21$. Jeevan purchased $4$ pens of $A$ variety, $3$ pens of $B$ variety and $2$ pens of $C$ variety for \rupee $60$. While Shikha purchased $6$ pens of $A$ variety , $2$ pens of $B$ variety and $3$ pens of $C$ variety for \rupee $70$. Using matrix method, find cost of each variety of pen.
\hfill (10, 2016)
    \item On her birthday Seema decided to donate some money to children of an orphanage home. If there were $8$ children less, every one would have got \rupee $10$ more. However, if there were $16$ children more, every one would have got \rupee $10$ less. Using matrix method, find the number of children and the amount distributed by Seema. What values are reflected by Seema's decision ?
\hfill (10, 2016)
    \item A trust invested some money in two type of bonds. The first bond pays $10$\% interest and second bond pays $12$\% interest. The trust received \rupee $2,800$ as interest. However, if trust had interchanged money in bonds, they would have got \rupee $100$ less as interest. Using matrix method, find the amount invested by the trust. Interest received on this amount will be given to an {\em ashram} as donation. Which value is reflected in this question ?
\hfill (10, 2016)
\item A trust fund has \rupee $35,000$ is to be invested in two different types of bonds. The first bond pays $8\%$ interest per annum which will be given to a {\em matha} and second bond pays $10\%$ interest per annum which will be given to a temple. Using matrix multiplication, determine how to divide \rupee $35,000$ among two types of bonds if the trust fund obtains an annual total interest of \rupee $3,200$. What are the values reflected in this question? 
\hfill (10, 2016)


\end{enumerate}
