\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item For what value of $k$, the system of linear equations
      \begin{align*}
          x+y+z    & = 2 \\
          2x+y-z   & =3  \\
          3x+2y+kz & =4
      \end{align*}
      has a unique solution? \hfill (12, 2016)
\item The pair of linear equations
$\frac{3x}{2}+\frac{5y}{3}=7$ and $9x+10y=14$ is
\begin{enumerate}[label=(\alph*)]
\item consistent
\item inconsistent
\item consistent with one solution 
\item consistent with many solutions 
\end{enumerate}
\hfill (12, 2020)
\item Solve the equation $x+2y=6$ and $2x-5y=12$ graphically.
\hfill (10, 2022)
\item Solve the following equations for $x$ and $y$ using cross-multiplication method
	\begin{align*}
		(ax-by)+(a+4b)=0 \\
                (bx+ay)+(b-4a)=0
	\end{align*}
\hfill (10, 2022)
	\item The pair of linear equations $ 2x=5y+6 $ and $ 15y=6x-18 $ represents two lines which are  
\begin{enumerate}
    \item intersecting
    \item parallel
    \item coincident
    \item either intersecting or parallel
\end{enumerate}
\hfill (10, 2023)
\item If the pair of equations $3x - y + 8 = 0$ and $6x - ry +16 =0$ represents coincident lines, then the value of $r$ is \rule{1cm}{0.2pt}.
\hfill (10, 2023)
\item If the system of linear equations 
$2x + 3y = 7$  and   $2ax +\brak{a + b}y =28$ 
have infinite number of solutions, then find the values of $a$ and $b$.
\hfill (10, 2023)
\item  If $217x + 131y = 913$ and  
$131x + 217y = 827$,  then solve the equations for the values of $x$ and $y$.
\hfill (10, 2023)
    \item If $\myvec{2 & 0 \\5 & 4} = \vec{P} + \vec{Q}$ 
	    is a symmetric and $\vec{Q}$ is a skew symmetric matrix, then $\vec{Q}$ is equal to \rule{1cm}{0.2pt}.
\hfill (12, 2023)
    \item If $\vec{A}=\myvec{ -3 & -2 & -4\\2 & 1 & 2\\2 & 1 & 3}$
and $\vec{B} =\myvec{  1 & 2 & 0\\-2 & -1 & -2\\0 & -1 & 1}$, then find $AB$ and use it to solve the following system of equations 
\begin{align*} x - 2y &= 3\\2x - y - z &= 2\\-2y + z &= 3\end{align*}
\hfill (12, 2023)
    \item Find whether the following pair of linear equations are consistent or inconsistent
    \begin{align*}
     5x - 3y = 11, -10x + 6y = 22.
    \end{align*}
\hfill (10, 2021)
    \item Solve for $x$ and $y$
    \begin{align*}
    x + y = 6, 2x - 3y = 4.
    \end{align*}
\hfill (10, 2021)
    \item Find out whether the pair of equations $2x + 3y = 0$ and $2x - 3y = 26$ is consistent or inconsistent.
\hfill (10, 2021)
    
    \item For what values of $k$, does the pair of linear equations $kx - 2y = 3$ and $3x + y = 5$ have a unique solution?
\hfill (10, 2021)
    
    \item What type of lines will you get by drawing the graph of the pair of equations $x - 2y + 3 = 0$ and $2x - 4y = 5$?
\hfill (10, 2021)
    \item Find the value of $k$ for which the system of equations $x + 2y = 5$ and $3x + ky + 15 = 0$ has no solution.
\hfill (10, 2021)
    \item Solve the system of linear equations using the matrix method
    \begin{align*}
        7x + 2y &= 11 \\
        4x - 7y &= 2
    \end{align*}
\hfill (12, 2021)
\item Using matrix method, solve the following system of equations 
\begin{align*}
    2x-3y+5z&=13\\
    3x+2y-4z &=-2\\
    x+y-2z&=-2.
\end{align*}
\hfill (12, 2019)
\item Using matrices solve the following system of linear equations
	\begin{align*}
		    2x+3y+10z&=4\\4x+6y+5z&=1\\6x+9y-20z&=2
	\end{align*}       
\hfill (12, 2019)
\item Find the solution of the pair of equations 
\begin{align*}
    \frac{3}{x}+\frac{8}{y}=-1; \frac{1}{x}-\frac{2}{y}=2, x, y\neq 0
\end{align*}
\hfill (10, 2019)

\item Find the value(s) of $k$ for which the pair of equations
\begin{align*}
    kx+2y=3\\
3x+6y=10
\end{align*}
has a unique solution.
\hfill (10, 2019)
 \item Find the value(s) of $k$ so that the pair of equations $x + 2y = 5$ and $3x + ky + 15 = 0$ has a unique solution.
\hfill (10, 2019)

 \item For what value of $k$, will the following pair of equations have infinitely many solutions 
\begin{align*}
	2x + 3y = 7 \hspace{2pt} \text{and} \hspace{2pt} \brak{k+2}x - 3\brak{1-k}y = 5k+1 
\end{align*}
\hfill (10, 2019)

\item Solve the following pair of linear equations 
\begin{align*}
 3x - 5y = 4\\
2y + 7 = 9x   
\end{align*}    
\hfill (10, 2019)

\item Solve the following pair of linear equations 
\begin{align*}
 3x + 4y = 10\\
2x - 2y = 2   
\end{align*}    
\hfill (10, 2019)
\item For what value of $k$, does the system of linear equations
\begin{align*}
   2x + 3y = 7\\
 \brak{k - 1} x + \brak{k + 2} y = 3k
\end{align*}
have an infinite number of solutions ?
\hfill (10, 2019)
\item Using matrices, solve the following system of linear equations 
	\begin{align*}
		x+2y-3z=-4\\
		2x+3y+2z=2\\
		3x-3y-4z=11.
	\end{align*}
\hfill (12, 2018)
\item Determine the product	$\myvec{-4 & 4 & 4\\-7 & 1 & 3\\5 & -3 & -1}$ $\myvec{1 & -1 &  1\\1 & -2 & -2\\2 &  1 &  3}$ and use it to solve the system of equations 

\begin{align*}
	x-y+z&=4\\
	x-2y-2z&=9
	\\
	2x+y+3z&=1 .
\end{align*}
\hfill (12, 2017)
\item Solve the equations $x+2y=6$ and $2x-5y=12$ graphically. \hfill (12, 2022)
\item Solve the system of linear equations, using matrix method  
\begin{align*}
  7x + 2y &= 11\\
  4x - y &= 2
\end{align*}
\hfill (12, 2021)
\item Find the value of $k$ for which the following pair of linear equations have infinitely many solutions. 
\begin{align*}
	2x+3y&=7
	\\
	(k+1)x+(2k-1)y&=4k+1
\end{align*}
\hfill (10, 2019)

\end{enumerate}
