Form the pair of linear equations in the following problems and find their solutions graphically
\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item A trust fund has \rupee30000 that must be invested in two different types of bonds.  The first bond pays $5\%$  interest per year,  and the second bond pays $7\%$ interest per year.   Determine how to divide \rupee30000 among the $2$ types of bonds.  If the trust fund must obtain an annual total interest of
\begin{enumerate}
\item \rupee1800
\item \rupee2000
\end{enumerate}
\solution
		\input{chapters/appl/1.tex}
\item $10$ students of Class X took part in a Mathematics quiz.  If the number of girls is $4$ more than the number of boys,  find the number of boys and girls who took part in the quiz. 
\item $5$ pencils and $7$ pens together cost \rupee $50$ whereas $7$ pencils and $5$ pens together cost  \rupee $  46$.  Find the cost of one pencil and that of one pen. 
\item Half the perimeter of a rectangular garden,  whose length is $4m$,  more than its width,  is $36m$.  Find the dimensions of the garden. 
\item A part of monthly hostel charges is fixed and the remaining depends on the number of days one has taken food in the mess.  When a student $A$ takes food for $20$ days she has to pay \rupee $1000$ as hostel charges whereas a student $B$ who takes food for $26$ days,  pays \rupee $1180$ as hostel charges.  Find the fixed charges and the cost of food per day. 
\item A fraction becomes $\frac{1}{3}$ when $1$ is subtracted from the numerator and it becomes $\frac{1}{4}$ when $8$ is added to the denominator.  Find the fraction. 
\item Yash scored $40$ marks in a test,  getting $3$ marks for each right answer and losing $1$ mark for each wrong answer.  Had $4$ marks been awarded for each correct answer and $2$ marks been deducted for each incorrect answer,  then Yash would have scored $50$ marks.  How many questions were there in the test?
\item Places $A$ and $B$ are $100km$ apart on a highway.  One car starts from $A$ and another from $B$ at the same time.  If the car travel in the same direction at different speeds,  they meet in $5$hrs.  If they travel towards each other,  they meet in $1$hr.  What are the speeds of the two cars?
\item The area of a rectangle gets reduced by $9$ square units,  if its length is reduced by $5$ units and breadth is increased by $3$ units.  If we increase the length by $3$ units and the breadth by $2$ units,  the area increases by $67$ square units.  Find the dimensions of the rectangle. 
\item Narayan tells his daughter,  `Seven years ago,  I was seven times as old as you were then.  Also,  $3$ years from now,  I shall be $3$ times as old as  you will be.' Find their ages.  
\item The coach of a cricket team buys $3$ bats and $6$ balls for  \rupee $ 3900$.  Later,  she buys another bat and $3$ more balls of the same kind for  \rupee $ 3300$.  Find the cost of a bat and ball. 
\item The cost of $2kg$ of apples and $1kg$ of grapes on a day was found to be  \rupee $ 160$.  After a month,  the cost of $4kg$ of apples and $2kg$ of grapes is  \rupee $ 300$.  Assuming that the costs remain unchanged,  find the cost of a kg of apples and grapes.  
    \item The difference between two numbers is $26$ and one number is three times the other.  Find them. 
    \item The larger of two supplementary angles exceeds the smaller by $18$ degrees.  Find them. 
    \item The coach of a cricket team buys $7$ balls and $6$ balls for \rupee3800.  Later,  she buys $3$ bats and $5$ balls for \rupee1750.  Find the cost of each bat and each ball. 
    \item The taxi charges in a city consist of a fixed charge together with the charges for the distance covered.  For a distance of $10$ km,  the charge paid is \rupee105 and for a distance of $15$ km,  the charge paid is \rupee155.  What are the fixed charges and the charge per km? How much does a person have to pay for travelling a distance of 25 km ? 
    \item A fraction becomes $\frac{9}{11}$ if $2$ is added to both the numerator and the denominator.  If $3$ is added to both the numerator and the denominator,  it becomes $\frac{5}{6}$.  Find the fraction. 
    \item Five years hence,  the age of Rahul will be three times that of his son.  Five years ago,  Rahul's age was seven times that of his son.  What are their present ages?
\item If we add $1$ to the numerator and subtract $1$ from the denominator,  a fraction reduces to $1$.  It becomes $\frac{1}{2}$ if we only add $1$ to the denominator.  What is the fraction?
\item Five years ago,  Minu was thrice as old as Sonu.  Ten years later,  Minu will be twice as old as Sonu.  How old are Minu and Sonu?
\item The Sum of the digits of a two-digit number is $9$.  Also,  nine times this number is twice the number obtained by reversing the order of the digits.  Find the number. 
\item Meena went to a bank to withdraw \rupee2000.  She asked the cashier to give her \rupee50 and \rupee100 notes only.  Meena got $25$ notes in all.  Find how many notes of \rupee50 and \rupee100 she received. 
\item A lending library has a fixed charge for the first three days and an additional charge for each day thereafter.  Sarita paid \rupee27 for seven days,  while Susheela paid \rupee21 for five days.  Find the fixed charge and the charge for each extra day.   
\item The ages of two friends Ani and Bijoya differ  by $3$  years.  Ani's father Dharam is twice as old as Ani and Bijoya is twice as old as sister Kanta.  The ages of Kanta and Dharam differ by $30$ years.  Find the ages of Ani and Bijoya. 
\item  One says,  \textquotedblleft Give me a hundred,  Friend!  I shall then become twice as rich as you \textquotedblright.  The other \textquotedblleft  if you give me ten,  i shall be six times as rich as you \textquotedblright.   Tell me What is the amount of their (respective) capital? [From the bijaganita of Bhaskara II].  
\item A train covered a certain distance at a uniform speed.  If the train would have been 10 km/h faster,  it would have taken $2$ hours less than the scheduled time.  And,  if the train were slower by 10 km/h; it would have taken $3$ hours more than the scheduled time.  Find the distance covered by the train. 
\item The students of a class are made to stand in rows.  If 3 students are extra in a row,  there would be $1$ row less.  If $3$ students are less in a row,  there would be $2$ rows more.  Find the number of students in the class. 
\item Ritu can row downstream $20km$ in $2$ hours, and upstream $4km$ in $2$ hours. Find her speed of rowing in still water and the speed of the current. 
\item $2$ women and $5$ men can together finish an embroidery work in $4$ days,  while $3$ women and $6$ men can finish it in $3$ days.  Find the time taken by $1$ women alone to finish the work, and also that taken by $1$ man alone. 
\item Rambha travels $300 km$ to her home partly by train and partly by bus. She takes $4$ hours if she travels $60km$ by train and the remaining by bus. If she travels $100km$ by train and the remaining by bus,  she takes $10$ minutes longer. Find the speed of the train and the bus seperately
\item In a $\triangle ABC,  \angle C=3 \angle B=2(\angle A+\angle B)$.  Find the three angles. 
\item $ABCD$ is a cyclic quadrilateral 
	with angles
\begin{align}
	A = 4y+20,  B = -7x+5,  C = -4x,  D = 3y-5. 
\end{align}
Find them.  
\item Draw the graphs of the equations $5x-y=5$ and $3x-y=3$.  Determine the Co-ordinates of the vertices of the triangle formed by these lines and the $y$ axis. 
\item Draw the graphs of the equations $x-y+1=0$ and $3x+2y-12=0$.  Determine the coordinates of the vertices of the triangle formed by these lines and the axis and shade the triangular region. 
\item The cost of $4 kg$ onion, $3 kg$ wheat and $2 kg$ rice is \rupee60. The cost of $2 kg$ onion, $4 kg$ wheat and $6 kg$ rice is \rupee90. The cost of $6 kg$ onion, $2 kg$ wheat and $3 kg$ rice is \rupee70. Find cost of each item per kg. 
\item Romila went to a stationary shop and purchased $2$ pencils and $3$ erasers for \rupee9. Her friend Sonali saw the new variety of pencils and erasers with Romila, and she also bought $4$ pencils and $6$ erasers of the same kind for \rupee18. Represent this situation algebraically and graphically.
\item Champa went to a ``Sale" to purchase some pants and skirts. When her friends asked her how many of each she had boughtc she answered, ``The number of skirts is two less than twice the number of pants purchased. Also, the number of skirts is four less than four times the number of pants purchased". Help her friends to find how many pants and skirts Champa bought.
\item 
Alwar tells his daughter, ``Seven years ago, I was seven times as old as you were then. Also, three years from now, I shall be three times as old as you will be."   Represent this situation algebraically and graphically.
\item The cost of 2 pencils and 3 erasers is \rupee9 and the cost of 4 pencils and 6 erasers is \rupee18. Find the cost of each pencil and each eraser.
\item The ratio of incomes of two persons is 9:7 and the ratio of their expenditures is $4:3$. If each of them manages to save \rupee2000 per month, find their monthly incomes.
\item The sum of a two digit number and the number obtained by reversing the digits is $66$. If the digits of the number differ by 2, find the number. How many such numbers are there?
\item A boat goes $30$ km upstream and $44$ km downstream in $10$ hours. In $13$ hours, it can go $40$ km upstream and $55$ km down-stream. Determine the speed of the stream and that of the boat in still water.
\item The sum of three numbers is $6$. If we multiply the third number by $3$ and add the second number to it, we get $11$. By adding the first and third numbers, we get double of the second number. Find the numbers. 
\end{enumerate}
