\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item  Reduce the following equations into normal form. Find their perpendicular distances from the origin and angle between perpendicular and the positive $x$-axis.
\label{chapters/11/10/3/3}
\begin{enumerate}
	\item $x-\sqrt{3}y+8=0$ 
	\item $y-2=0$
	\item $x-y=4$
\end{enumerate}
\solution
\input{chapters/11/10/3/3/perp.tex}
 \item  In each of the following cases, determine the direction cosines of the normal to
the plane and the distance from the origin.
\begin{enumerate}
	\item $z=2$ 
	\item $x + y + z = 1$
	\item $2x + 3y – z = 5$
	\item $5y + 8 = 0$
\end{enumerate}
    \solution
		\input{chapters/12/11/3/1/dist.tex}
\item Find the distance of the point $(-1,1)$ from the line $12\brak{x+6} = 5\brak{y-2}$. 
\label{chapters/11/10/3/4}
	\\
\solution 
\input{chapters/11/10/3/4/line.tex}
\item Find the coordinates of the foot of the perpendicular from $(-1, 3)$ to the line $3x-4y-16=0$.  
\label{chapters/11/10/3/14}
\\
\solution
\input{chapters/11/10/3/14/line.tex}
\item  If ${p}$ and ${q}$ are the lengths of perpendiculars from the origin to the lines ${x}\cos\theta - {y}\sin\theta =  {k}\cos2\theta$ and ${x}\sec\theta + {y}\cosec\theta = {k}$, respectively, prove that ${p}^2 + 4{q}^2 = {k}^2$
\label{chapters/11/10/3/16}
\\
\solution
\input{chapters/11/10/3/16/line.tex}
\item In the triangle $ABC$ with vertices $\vec{A} \brak{2, 3}$, $\vec{B} \brak{4, –1}$ and $\vec{C} \brak{1, 2}$, find the equation and length of altitude from the vertex $\vec{A}$.
\label{chapters/11/10/3/17}
\\
\solution
\input{chapters/11/10/3/17/line.tex}
\item If $p$ is the length of perpendicular from origin to the line whose intercepts on the axes are $a$ and $b$, then show that 
\begin{align}
	\frac{1}{p^2} = \frac{1}{a^2}+ \frac{1}{b^2}
\label{eq:11/10/3/18}
\end{align}
\label{chapters/11/10/3/18}
\\
\solution
\input{chapters/11/10/3/18/dist.tex}
\item Find the points on the x-axis, whose distances from the line $\frac{x}{3}+\frac{y}{4}=1$ are 4 units.
\label{chapters/11/10/3/5}
	\\
	\solution
\input{chapters/11/10/3/5/line.tex}
\item What are the points on the y-axis whose distance from the line $\frac{x}{3}+\frac{y}{4}=1$ is 4 units.
\\
\solution
		\input{chapters/11/10/4/4/line.tex}
\item Find perpendicular distance from the origin to the line joining the points $(\cos\theta,\sin\theta)$ and $(\cos\phi,\sin\phi)$.
\\
\solution
		\input{chapters/11/10/4/5/dist.tex}
\item Find the distance between parallel lines
\label{chapters/11/10/3/6}
\begin{enumerate}
	\item $15x+8y-34=0$ and  $15x+8y+31=0$ \\
	\item  $l(x+y)+p=0$ and  $l(x+y)-r=0$
\end{enumerate}
	\solution
\input{chapters/11/10/3/6/dist.tex}
\item Find the equation of line which is equidistant from parallel lines $9x+6y-7=0$ and $3x+2y+6=0$.
\\
\solution
		\input{chapters/11/10/4/21/line.tex}
	\item Prove that the products of the lengths of the perpendiculars drawn from the points $\myvec{\sqrt{a^2-b^2}& 0}^{\top}$ and $\myvec{-\sqrt{a^2-b^2} &0}^{\top}$ to the line $\frac{x}{a} \cos{\theta} + \frac{y}{b}\sin{\theta} =1 $ is $ b^2 $.
\\
    \solution 
		\input{chapters/11/10/4/23/dist.tex}
	\item The distance of the point $\vec{P}(2, 3)$ from the x-axis is

\begin{enumerate}
\item 2
\item 3
\item 1
\item 5 
\end{enumerate}

\item Find the foot of perpendicular from the point $(2,3,-8)$ to the line  $\dfrac{4-x}{2}=\dfrac{y}{6}=\dfrac{1-z}{3}$.Also, find the perpendicular distance from the given point to the line.
\item Find the distance of a point $(2,4,-1)$ from the line $$\frac{x+5}{1}=\frac{y+3}{4}=\frac{z-6}{-9}$$
\item Find the length and the foot of perpendicular from the point $ \brak{1,\dfrac{3}{2} ,2 }$ to the plane $2x-2y+4z+5=0.$
\item Show that the points $(\hat{i}-\hat{j}+3\hat{k})$ and $3(\hat{i}+\hat{j}+\hat{k})$ are equidistant from the plane $\overrightarrow{r} \cdot (5\hat{i}+2\hat{j}-7\hat{k})+9=0$ and lies on opposite side of it.
\item The distance of the plane $\overrightarrow{r} \cdot \brak{ \dfrac{2}{7}\hat{i}+\dfrac{3}{7}\hat{j}-\dfrac{6}{7}\hat{k}}=1$ from the origin is 
\begin{enumerate}
	\item 1
	\item 7
	\item $\dfrac{1}{7}$
	\item None of these	
\end{enumerate}
\item If the foot of perpendicular drawn from the origin to a plane is $(5,-3,-2)$, then the equation of plane is $\overrightarrow{r} \cdot (5\hat{i}-3\hat{j}-2\hat{k})=38.$
\item Find the equation of line  drawn perpendicular to the line $\frac{x}{4}+\frac{y}{6}=1$ through the point where it meets the y-axis \\
\solution
		\input{chapters/11/10/4/7/line.tex}
\item Find the equation of line whose perpendicular distance from the origin is 5 units and the angle made by the perpendicular with the positive $x$-axis is $30\degree$.
\label{chapters/11/10/2/8}
\\
\solution
\input{chapters/11/10/2/8/line.tex}
\item 
	Find the equation of the line passing through  (-3,5) and perpendicular to the line through the points (2,5) and (-3,6).
	\\
	\solution 
\label{chapters/11/10/2/10}
\input{chapters/11/10/2/10/line.tex}
\item 
	The perpendicular from the origin to a line meets it at the point $(-2,9)$. Find the equation of the line.
\label{chapters/11/10/2/15}
	\\
	\solution
\input{chapters/11/10/2/15/line.tex}
\item Find the equation of line perpendicular to the line $x-7y+5=0$ and having $x$ intercept $3$\\
\label{chapters/11/10/3/8}
\solution
\input{chapters/11/10/3/8/line.tex}
	\item Find the equation of the line passing through the point $\brak{1,2,-4}$ and perpendicular to the two lines
\begin{align}
	\frac{x-8}{3}=\frac{y+19}{-16}=\frac{z-10}{7} \text{ and }\\ \frac{x-15}{3}=\frac{y-29}{8}=\frac{z-5}{-5} 
\end{align}
    \solution
		\input{chapters/12/11/4/20/line.tex}
 \item The perpendicular from the origin to the line $y=mx+c$ meets it at the point $(-1,2)$. Find the values of m and c.
 \label{11.10.3.15}
	 \\
 \solution
 \input{chapters/11/10/3/15/vector.tex}
\item  Point $\vec{P}(0,2)$ is the point of intersection of $y$-axis and perpendicular bisector of line segment joining the points $\vec{A}(-1,1) \text{ and } \vec{B}(3,3)$
\item 
A line perpendicular to the line segment joining the points $\vec{P}(1,0)$ and $\vec{Q}(2,3)$ divides it in the ratio $1:n$. Find the equation of the line.
	\\
	\solution 
\label{chapters/11/10/2/11}
\input{chapters/11/10/2/11/line.tex}
\item Find the vector equation of a plane which is at a distance of 7 units from the origin and normal to the vector $3\hat{i}+5\hat{j}-6\hat{k}$.
	\\
    \solution
		\input{chapters/12/11/3/2/norm.tex}
\item Find the equation of a plane which is at a distance 3$\sqrt{3}$ units from origin and the normal to which is equally inclined to coordinate axis.
\item If the line drawn from the point $(-2,-1,-3)$ meets a plane at right angle at the point $(1,-3,3)$, find the equation of the plane.
\item O is the origin and A is $(a,b,c)$.Find the direction cosines of the line OA and the equation of plane through A at right angle at OA.
\item Two systems of rectangular axis have the same origin. If a plane cuts them at distances $a,b,c$ and $a^{\prime},b^{\prime},c^{\prime}$, respectively, from the origin, prove that $$\frac{1}{a^2}+\frac{1}{b^2}+\frac{1}{c^2}=\frac{1}{{a^{\prime}}^2}+\frac{1}{{b^{\prime}}^2}+\frac{1}{{c^{\prime}}^2}$$.
\item Find the equation of the plane through the points $(2,1,-1)$ and $(-1,3,4),$ and 
perpendicular to the plane $x-2y+4z=10.$
	\item Find the values of $\theta \text{ and } p$, if the equation $x\cos\theta+y\sin\theta=p$ is the normal form
of the line $\sqrt{3}x+y+2=0$.
\\
\solution
		\input{chapters/11/10/4/2/line.tex}
\end{enumerate}
