\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item 
\label{chapters/10/11/2/6}
Let $ABC$ be a right triangle in which $AB = 6 cm, BC = 8 cm$ and $\angle B = 90\degree$. $BD$ is the perpendicular from $\vec{B}$ on $AC$. The circle through $\vec{B}, \vec{C}, \vec{D}$ is drawn. Construct the tangents from $\vec{A}$ to this circle.
\item 
	Draw a line segment $AB$ of length 8cm. Taking $\vec{A}$ as centre, draw a circle of radius 4cm and taking $\vec{B}$ as centre, draw another circle of radius 3cm. Construct tangents to each circle from the centre of the circle.
\label{chapters/10/11/2/5}
\item 
	Draw a pair of tangents to a circle of radius 5 cm which are inclined to each other at an angle of 60\degree.
\label{chapters/10/11/2/4}
\item 
Draw a circle of radius 3 cm. Take two points $\vec{P}$ and $\vec{Q}$ on one of its extended diameter each at a distance of 7 cm from its centre. Draw tangents to the circle from these two points $\vec{P}$ and $\vec{Q}$.
\label{chapters/10/11/2/3}
\item 
	Construct a tangent to a circle of radius 4cm from a point on the concentric circle of radius 6cm and measure its length. Also verify the measurement by actual calculation.
\label{chapters/10/11/2/2}
\item From a point $\vec{Q}$, the length of the tangent to a circle is $24 cm$ and the distance of $\vec{Q}$ from the centre is $25 cm$. Find the radius of the circle. Draw the circle and the tangents. 
\label{chapters/10/10/2/1}
\item To draw a pair of tangents to a circle which are inclined to each other at an angle of $60\degree$, it is required
to draw tangents at end points of those two radii of the circle, the angle between them should be 
\begin{enumerate}
\item $135\degree$
\item $90\degree$
\item $60\degree$
\item $120\degree$ 
\end{enumerate}
\item Draw two concentric circles of radii 3 cm and 5 cm. Taking a point on outer circle construct the pair of tangents to the other. Measure the length of a tangent and verify it by actual calculation.
\item Draw a circle of radius 4 cm .Construct a pair of tangents to it, the angle detween which is $60\degree$. Also justify the construction. Measure the distance between the centre of the circle and the point of intersection of tangents.
\item Construct a tangent to a circle of radius 4 cm from a point which is at a distance of 6 cm from its centre.
\end{enumerate}
Write True or False and give reasons for your answer in each of the following 
\begin{enumerate}[resume*]
\item A pair of tangents can be constructed from a point $\vec{h}$ to a circle of radius 3.5 cm situated at a distance of 3 cm from the centre.
\item A pair of tangents can be constructed to a circle inclined at an angle of $170\degree$.
	\item Draw a circle of radius 2.5 cm. Take a point $\vec{P}$ outside the circle at a distance of 7 cm from the center. Then construct a pair of tangents to the circle from point $\vec{P}$.
\hfill (10, 2022)

	\item Write the steps of construction for constructing a pair of tangents to a circle of radius 4 cm from a point $\vec{P}$, at a distance of 7 cm from its center $\vec{O}$.
\hfill (10, 2022)
	\item Draw a pair of tangents to a circle of radius $4 cm$ which are inclined to each other at an angle of 45\degree.	
\hfill (10, 2021)
	\item Draw a circle of radius $5 cm$. From a point $8 cm$ away from its centre, construct a pair of tangents to the circle.
\hfill (10, 2021)
	\item Write the steps of construction of a circle of diameter $6 cm$ and drawing of a pair of tangents to the circle from a point $5 cm$ away from the centre.
\hfill (10, 2021)
\item Draw two concentric circles of radii $2 cm$ and $5 cm$. Take a point $P$ on the outer circle and construct a pair of tangents $PA$ and $PB$ to the smaller circle. Measure $PA$.  
\hfill (10, 2019)
    \item Draw a pair of tangents to a circle of radius $3$ cm, which are inclined to each other at an angle of 60\degree.
\hfill (10, 2011)
\end{enumerate}
